
```{r}
library(dplyr)
library(xgboost)
library(OptimalCutpoints)
library(caret)
library(SHAPforxgboost)
#source("a_insights_shap_functions.r")
library(ggplot2)
library(parallel)
library(xgboostExplainer)
```

```{r}
load("PredictionData.RData")
```

```{r}
#Log was done without accounting for 0, redoing
PredictionData <- PredictionData %>% mutate(PPG_Diff_ABS_log = log(PPG_Diff_ABS + 1)
         ,Expected_Goals_Diff_ABS_log = log(Expected_Goals_Diff_ABS + 1)
         ,USAT_weighted_Diff_ABS_log = log(USAT_weighted_Diff_ABS + 1)
         ,FOP_weighted_Diff_ABS_log = log(FOP_weighted_Diff_ABS + 1)
         ,SpecialTeamsValue_log = log(SpecialTeamsValue + 1)
         ,ContractDifference_ABS_log = log(ContractDifference_ABS + 1)) 
```


```{r}
#Create weighted 80/20 split
set.seed(42)
train.index <- createDataPartition(PredictionData$OT, p = .8, list = FALSE)
train_db <- PredictionData[ train.index,]
test_db  <- PredictionData[-train.index,]

summary(as.factor(train_db$OT))
summary(as.factor(test_db$OT))
```

```{r}
train_db <- train_db %>% select(-GameKey, -PPG_Diff_ABS, -Expected_Goals_Diff_ABS, -USAT_weighted_Diff_ABS, -FOP_weighted_Diff_ABS, -SpecialTeamsValue, -ContractDifference_ABS) 

test_db <- test_db %>% select(-GameKey, -PPG_Diff_ABS, -Expected_Goals_Diff_ABS, -USAT_weighted_Diff_ABS, -FOP_weighted_Diff_ABS, -SpecialTeamsValue, -ContractDifference_ABS) 
```


#### Preparing for XGBoost
```{r}
dtrain <- xgb.DMatrix(data = as.matrix(train_db %>% select(-OT)), label = train_db$OT)
dtest <- xgb.DMatrix(data = as.matrix(test_db %>% select(-OT)), label = test_db$OT)
```

```{r}
set.seed(42)
initial_mod <- xgboost(data = dtrain, # Set training data
               
               nrounds = 100, # Set number of rounds
               
               verbose = 1, # 1 - Prints out fit
               print_every_n = 20, # Prints out result every 20th iteration
 
               
               objective = "binary:logistic", # Set objective
               eval_metric = "error",
               eval_metric = "auc") # Set evaluation metric to use


boost_preds <- predict(initial_mod, dtest) # Create predictions for xgboost model

#check error
err <- mean(as.numeric(boost_preds > 0.5) != test_db$HomeTeamWin)

#current error is 0.4432624....
#so we immediately can predict to a 55% accuracy
#reduced to 0.44188... after strat sampling

```
```{r}
boost_preds <- predict(initial_mod, dtrain) # Create predictions for xgboost model
# Join predictions and actual
pred_dat <- cbind.data.frame(boost_preds , train_db$OT)
names(pred_dat) <- c("predictions", "response")
oc<- optimal.cutpoints(X = "predictions",
                       status = "response",
                       tag.healthy = 0,
                       data = pred_dat,
                       methods = "MaxEfficiency")

boost_preds_1 <- predict(initial_mod, dtest) # Create predictions for xgboost model

pred_dat <- cbind.data.frame(boost_preds_1 , test_db$OT)#
# Convert predictions to classes, using optimal cut-off
boost_pred_class <- rep(0, length(boost_preds_1))
boost_pred_class[boost_preds_1 >= oc$MaxEfficiency$Global$optimal.cutoff$cutoff[1]] <- 1


t <- table(boost_pred_class, actual = test_db$OT) # Create table
confusionMatrix(t, positive = "1") # Produce confusion matrix
```
Pos Pred Value is our goal: can we get that to over .33?


#time to tune

#### Checking the number of rounds
```{r}
set.seed(42)
bst_nrounds <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
               eta = 0.01, # Set learning rate
              
               nrounds = 1000, # Set number of rounds
               early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
              print_every_n = 20, # Prints out result every 20th iteration
               
                verbose = 1, # 1 - Prints out fit
               nthread = 1, # Set number of parallel threads
                
              
               objective = "binary:logistic", # Set objective
               eval_metric = "aucpr",
               #eval_metric = "error" # Set evaluation metric to use
)
```


Best was 141. Test with 200 rounds and 20 for early stop

#minchild and max depth
```{r}
# Be Careful - This can take a very long time to run
max_depth_vals <- c(3, 5, 7, 10, 15, 20) # Create vector of max depth values
min_child_weight <- c(1,3,5,7,10,15, 17, 20, 25, 30, 35, 40, 45, 50) # Create vector of min child values

#its liking high min_child and low max_depth
#current best: max_depth: 3 min_child: 30

# Expand grid of parameter values
cv_params <- expand.grid(max_depth_vals, min_child_weight)
names(cv_params) <- c("max_depth", "min_child_weight")
# Create results vector
aucpr_vec <- error_vec <- rep(NA, nrow(cv_params)) 
# Loop through results
for(i in 1:nrow(cv_params)){
  set.seed(111111)
  bst_tune <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.01, # Set learning rate
              max.depth = cv_params$max_depth[i], # Set max depth
              min_child_weight = cv_params$min_child_weight[i], # Set minimum number of samples in node to split
             
               
              nrounds = 200, # Set number of rounds
              early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
               
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr" # Set evaluation metric to use
              #,eval_metric = "error"
              ) # Set evaluation metric to use
  aucpr_vec[i] <- bst_tune$evaluation_log$test_aucpr_mean[bst_tune$best_ntreelimit]
  #error_vec[i] <- bst_tune$evaluation_log$test_error_mean[bst_tune$best_ntreelimit]
  
}
```



```{r}
# Join results in dataset
res_db <- cbind.data.frame(cv_params, aucpr_vec)
names(res_db)[3] <- c("aucpr") 
res_db$max_depth <- as.factor(res_db$max_depth) # Convert tree number to factor for plotting
res_db$min_child_weight <- as.factor(res_db$min_child_weight) # Convert node size to factor for plotting
# Print AUC heatmap
g_2 <- ggplot(res_db, aes(y = max_depth, x = min_child_weight, fill = aucpr)) + # set aesthetics
  geom_tile() + # Use geom_tile for heatmap
  theme_bw() + # Set theme
  scale_fill_gradient2(low = "blue", # Choose low color
    mid = "white", # Choose mid color
    high = "red", # Choose high color
    midpoint =mean(res_db$aucpr), # Choose mid point
    space = "Lab", 
    na.value ="grey", # Choose NA value
    guide = "colourbar", # Set color bar
    aesthetics = "fill") + # Select aesthetics to apply
  labs(x = "Minimum Child Weight", y = "Max Depth", fill = "AUCPR") # Set labels
g_2 # Generate plot
```
#only for 2nd error metric
```{r}
# print error heatmap
g_3 <- ggplot(res_db, aes(y = max_depth, x = min_child_weight, fill = error)) + # set aesthetics
  geom_tile() + # Use geom_tile for heatmap
  theme_bw() + # Set theme
  scale_fill_gradient2(low = "blue", # Choose low color
    mid = "white", # Choose mid color
    high = "red", # Choose high color
    midpoint =mean(res_db$error), # Choose mid point
    space = "Lab", 
    na.value ="grey", # Choose NA value
    guide = "colourbar", # Set color bar
    aesthetics = "fill") + # Select aesthetics to apply
  labs(x = "Minimum Child Weight", y = "Max Depth", fill = "Error") # Set labels
g_3 # Generate plot
```
```{r}
#res_db %>% arrange(error)
res_db %>% arrange(desc(aucpr))
#best is auc max_depth: 10 min_child: 10
#might have more with higher numbers, but stick with this for now
```

#best is max_depth: 20 min_child: 3

#gamma tuning
```{r}
gamma_vals <- c(0, 0.05, 0.1, 0.15, 0.2) # Create vector of gamma values

# Be Careful - This can take a very long time to run
set.seed(111111)
aucpr_vec <-  rep(NA, length(gamma_vals))
for(i in 1:length(gamma_vals)){
  bst_tune <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.01, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = gamma_vals[i], # Set minimum loss reduction for split

              
               
              nrounds = 200, # Set number of rounds
              early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
               
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr", # Set evaluation metric to use
              #,eval_metric = "error" # Set evaluation metric to use
  )
  aucpr_vec[i] <- bst_tune$evaluation_log$test_aucpr_mean[bst_tune$best_ntreelimit]
  #error_vec[i] <- bst_tune$evaluation_log$test_error_mean[bst_tune$best_ntreelimit]
  
}
```


```{r}
cbind.data.frame(gamma_vals, aucpr_vec)
```
# AUCpr best at 0.1

#redo number of trees to see if we need more
```{r}
set.seed(111111)
bst <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.01, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
             
               
              nrounds = 1000, # Set number of rounds
              early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
               
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr"
              #eval_metric = "error"
              ) # Set evaluation metric to use
```
#subsample and colsample
```{r}
# Be Careful - This can take a very long time to run
subsample <- c(0.5, 0.6, 0.7, 0.8, 0.9, 1) # Create vector of subsample values
colsample_by_tree <- c(0.5, 0.6, 0.7, 0.8, 0.9, 1) # Create vector of col sample values

# Expand grid of tuning parameters
cv_params <- expand.grid(subsample, colsample_by_tree)
names(cv_params) <- c("subsample", "colsample_by_tree")
# Create vectors to store results
aucpr_vec <- rep(NA, nrow(cv_params)) 
# Loop through parameter values
for(i in 1:nrow(cv_params)){
  set.seed(111111)
  bst_tune <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.01, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
              subsample = cv_params$subsample[i], # Set proportion of training data to use in tree
              colsample_bytree = cv_params$colsample_by_tree[i], # Set number of variables to use in each tree
               
              nrounds = 1000, # Set number of rounds
              early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
               
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr" # Set evaluation metric to use
              #,eval_metric = "error") # Set evaluation metric to use
  )
  aucpr_vec[i] <- bst_tune$evaluation_log$test_aucpr_mean[bst_tune$best_ntreelimit]
  #error_vec[i] <- bst_tune$evaluation_log$test_error_mean[bst_tune$best_ntreelimit]
  
}
```





```{r}
res_db <- cbind.data.frame(cv_params, aucpr_vec)
names(res_db)[3] <- c("aucpr") 
res_db$subsample <- as.factor(res_db$subsample) # Convert tree number to factor for plotting
res_db$colsample_by_tree <- as.factor(res_db$colsample_by_tree) # Convert node size to factor for plotting
g_4 <- ggplot(res_db, aes(y = colsample_by_tree, x = subsample, fill = aucpr)) + # set aesthetics
  geom_tile() + # Use geom_tile for heatmap
  theme_bw() + # Set theme
  scale_fill_gradient2(low = "blue", # Choose low color
    mid = "white", # Choose mid color
    high = "red", # Choose high color
    midpoint =mean(res_db$aucpr), # Choose mid point
    space = "Lab", 
    na.value ="grey", # Choose NA value
    guide = "colourbar", # Set color bar
    aesthetics = "fill") + # Select aesthetics to apply
  labs(x = "Subsample", y = "Column Sample by Tree", fill = "AUCPR") # Set labels
g_4 # Generate plot
```

# skip
```{r}
g_5 <- ggplot(res_db, aes(y = colsample_by_tree, x = subsample, fill = error)) + # set aesthetics
  geom_tile() + # Use geom_tile for heatmap
  theme_bw() + # Set theme
  scale_fill_gradient2(low = "blue", # Choose low color
    mid = "white", # Choose mid color
    high = "red", # Choose high color
    midpoint =mean(res_db$error), # Choose mid point
    space = "Lab", 
    na.value ="grey", # Choose NA value
    guide = "colourbar", # Set color bar
    aesthetics = "fill") + # Select aesthetics to apply
  labs(x = "Subsample", y = "Column Sample by Tree", fill = "Error") # Set labels
g_5 # Generate plot
```


```{r}
res_db %>% arrange(error)
res_db %>% arrange(desc(aucpr))
```

# subsample 0.5 colsample 0.5


#eta tuning - learning rate
```{r}
# Use xgb.cv to run cross-validation inside xgboost
set.seed(111111)
bst_mod_1 <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.3, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
              subsample = 0.5, # Set proportion of training data to use in tree
              colsample_bytree =  0.5, # Set number of variables to use in each tree
               
              nrounds = 1000, # Set number of rounds
              #early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
              
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr"
              #,eval_metric = "error" # Set evaluation metric to use
)
```
```{r}
# Use xgb.cv to run cross-validation inside xgboost
set.seed(111111)
bst_mod_2 <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.1, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
              subsample = 0.5, # Set proportion of training data to use in tree
              colsample_bytree =  0.5, # Set number of variables to use in each tree
               
              nrounds = 1000, # Set number of rounds
              #early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
              
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr"
              #eval_metric = "error" # Set evaluation metric to use
)
```
```{r}
# Use xgb.cv to run cross-validation inside xgboost
set.seed(111111)
bst_mod_3 <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.05, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
              subsample = 0.5, # Set proportion of training data to use in tree
              colsample_bytree =  0.5, # Set number of variables to use in each tree
               
              nrounds = 1000, # Set number of rounds
              #early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
              
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr",
              #eval_metric = "error") # Set evaluation metric to use
)
```
```{r}
# Use xgb.cv to run cross-validation inside xgboost
set.seed(111111)
bst_mod_4 <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.01, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
              subsample = 0.5, # Set proportion of training data to use in tree
              colsample_bytree =  0.5, # Set number of variables to use in each tree
               
              nrounds = 1000, # Set number of rounds
              #early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
              
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr",
              #eval_metric = "error" # Set evaluation metric to use
)
```
```{r}
# Use xgb.cv to run cross-validation inside xgboost
set.seed(111111)
bst_mod_5 <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.005, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
              subsample = 0.5, # Set proportion of training data to use in tree
              colsample_bytree =  0.5, # Set number of variables to use in each tree
               
              nrounds = 1000, # Set number of rounds
              #early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
              
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr",
              #eval_metric = "error") # Set evaluation metric to use
)

```
```{r}
# Use xgb.cv to run cross-validation inside xgboost
set.seed(111111)
bst_mod_6 <- xgb.cv(data = dtrain, # Set training data
              
              nfold = 5, # Use 5 fold cross-validation
               
              eta = 0.001, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
              subsample = 0.5, # Set proportion of training data to use in tree
              colsample_bytree =  0.5, # Set number of variables to use in each tree
               
              nrounds = 1000, # Set number of rounds
              #early_stopping_rounds = 200, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
              
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr"
              #,eval_metric = "error" # Set evaluation metric to use
)

```







```{r}
# Extract results for model with eta = 0.3
pd1 <- cbind.data.frame(bst_mod_1$evaluation_log[,c("iter", "test_aucpr_mean")], rep(0.3, nrow(bst_mod_1$evaluation_log)))
names(pd1)[3] <- "eta"
# Extract results for model with eta = 0.1
pd2 <- cbind.data.frame(bst_mod_2$evaluation_log[,c("iter", "test_aucpr_mean")], rep(0.1, nrow(bst_mod_2$evaluation_log)))
names(pd2)[3] <- "eta"
# Extract results for model with eta = 0.05
pd3 <- cbind.data.frame(bst_mod_3$evaluation_log[,c("iter", "test_aucpr_mean")], rep(0.05, nrow(bst_mod_3$evaluation_log)))
names(pd3)[3] <- "eta"
# Extract results for model with eta = 0.01
pd4 <- cbind.data.frame(bst_mod_4$evaluation_log[,c("iter", "test_aucpr_mean")], rep(0.01, nrow(bst_mod_4$evaluation_log)))
names(pd4)[3] <- "eta"
# Extract results for model with eta = 0.005
pd5 <- cbind.data.frame(bst_mod_5$evaluation_log[,c("iter", "test_aucpr_mean")], rep(0.005, nrow(bst_mod_5$evaluation_log)))
names(pd5)[3] <- "eta"
pd6 <- cbind.data.frame(bst_mod_6$evaluation_log[,c("iter", "test_aucpr_mean")], rep(0.001, nrow(bst_mod_6$evaluation_log)))
names(pd6)[3] <- "eta"
# Join datasets
plot_data <- rbind.data.frame(pd1, pd2, pd3, pd4, pd5, pd6)
# Converty ETA to factor
plot_data$eta <- as.factor(plot_data$eta)
# Plot points
g_6 <- ggplot(plot_data, aes(x = iter, y = test_aucpr_mean, color = eta))+
  geom_point(alpha = 0.5) +
  theme_bw() + # Set theme
  theme(panel.grid.major = element_blank(), # Remove grid
        panel.grid.minor = element_blank(), # Remove grid
        panel.border = element_blank(), # Remove grid
        panel.background = element_blank()) + # Remove grid 
  labs(x = "Number of Trees", title = "AUCPR v Number of Trees",
       y = "test_aucpr_mean", color = "Learning \n Rate")  # Set labels
g_6
```




```{r}
# Plot lines
g_7 <- ggplot(plot_data, aes(x = iter, y = test_aucpr_mean, color = eta))+
  geom_smooth(alpha = 0.5) +
  theme_bw() + # Set theme
  theme(panel.grid.major = element_blank(), # Remove grid
        panel.grid.minor = element_blank(), # Remove grid
        panel.border = element_blank(), # Remove grid
        panel.background = element_blank()) + # Remove grid 
  labs(x = "Number of Trees", title = "Error Rate v Number of Trees",
       y = "Error Rate", color = "Learning \n Rate")  # Set labels
g_7
```


```{r}
plot_data2 <- plot_data %>% filter(!eta %in% c("0.3", "0.1", "0.05"))
```


```{r}
# Plot lines
g_7_2 <- ggplot(plot_data2, aes(x = iter, y = test_error_mean, color = eta))+
  geom_smooth(alpha = 0.5) +
  theme_bw() + # Set theme
  theme(panel.grid.major = element_blank(), # Remove grid
        panel.grid.minor = element_blank(), # Remove grid
        panel.border = element_blank(), # Remove grid
        panel.background = element_blank()) + # Remove grid 
  labs(x = "Number of Trees", title = "Error Rate v Number of Trees",
       y = "Error Rate", color = "Learning \n Rate")  # Set labels
g_7_2
```


#make the model
```{r}
set.seed(111111)
bst_final <- xgboost(data = dtrain, # Set training data
              
        
               
              eta = 0.005, # Set learning rate
              max.depth = 20, # Set max depth
              min_child_weight = 3, # Set minimum number of samples in node to split
              gamma = 0.1, # Set minimum loss reduction for split
              subsample = 0.5, # Set proportion of training data to use in tree
              colsample_bytree =  0.5, # Set number of variables to use in each tree
               
              nrounds = 300, # Set number of rounds
              early_stopping_rounds = 50, # Set number of rounds to stop at if there is no improvement
               
              verbose = 1, # 1 - Prints out fit
              nthread = 1, # Set number of parallel threads
              print_every_n = 20, # Prints out result every 20th iteration
              
              objective = "binary:logistic", # Set objective
              eval_metric = "aucpr"#,
              #eval_metric = "error"
              ) # Set evaluation metric to use
```

```{r}
boost_preds <- predict(bst_final, dtrain) # Create predictions for XGBoost model on training data

pred_dat <- cbind.data.frame(boost_preds , train_db$OT)#
names(pred_dat) <- c("predictions", "response")
oc<- optimal.cutpoints(X = "predictions",
                       status = "response",
                       tag.healthy = 0,
                       data = pred_dat,
                       methods = "MaxEfficiency")

boost_preds <- predict(bst_final, dtest) # Create predictions for XGBoost model


#pred_dat <- cbind.data.frame(boost_preds , test_db$OT)#
# Convert predictions to classes, using optimal cut-off
boost_pred_class <- rep(0, length(boost_preds))
boost_pred_class[boost_preds >= oc$MaxEfficiency$Global$optimal.cutoff$cutoff[1]] <- 1


t <- table(boost_pred_class, actual = test_db$OT) # Create table
confusionMatrix(t, positive = "1") # Produce confusion matrix



```
