```{r}
library(dplyr)
library(lubridate)
library(stringr)
library(janitor)
library(caret)
```




```{r}
load("FO_Data.RData")
load("Goals_Data.RData")
load("Shots_Data.RData")
load("Misc_Data.RData")
load("PP_Data.RData")
```


```{r}
TeamInitlKey <- data.frame(Initl = c("BOS", "COL", "NSH", "LAK", "BUF", "WSH", "CHI", "SJS", "NYR", "PIT", "CAR", "WPG", "CBJ", "FLA", "ARI", "PHI", "ANA", "CGY", "NJD", "MIN", "DAL", "TOR", "MTL", "OTT", "DET", "TBL", "EDM", "VAN", "NYI", "SEA", "STL", "VGK", "UTA")
                             , Name = c("Boston Bruins" , "Colorado Avalanche","Nashville Predators","Los Angeles Kings","Buffalo Sabres","Washington Capitals","Chicago Blackhawks","San Jose Sharks","New York Rangers" ,"Pittsburgh Penguins","Carolina Hurricanes","Winnipeg Jets","Columbus Blue Jackets", "Florida Panthers","Arizona Coyotes","Philadelphia Flyers","Anaheim Ducks","Calgary Flames","New Jersey Devils","Minnesota Wild", "Dallas Stars","Toronto Maple Leafs","Montréal Canadiens","Ottawa Senators","Detroit Red Wings","Tampa Bay Lightning","Edmonton Oilers","Vancouver Canucks","New York Islanders","Seattle Kraken","St. Louis Blues","Vegas Golden Knights", "Utah Hockey Club"))
```




```{r}
FOAwayTeam <- FO_Data[grepl("@", FO_Data$game),]
FOHomeTeam <- FO_Data[!grepl("@", FO_Data$game),]

FOHomeTeam <- FOHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
FOHomeTeam <-  FOHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
FOHomeTeam <- left_join(FOHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

FOHomeTeam <- FOHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

FOHomeTeam <- FOHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))


FO_Data <- FOHomeTeam #just need home stats, away is relative to home and is calculated later

```

```{r}
#SAT_Data <- Shots_Data
SATAwayTeam <- Shots_Data[grepl("@", Shots_Data$game),]
SATHomeTeam <- Shots_Data[!grepl("@", Shots_Data$game),]

SATHomeTeam <- SATHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
SATHomeTeam <-  SATHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
SATHomeTeam <- left_join(SATHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

SATHomeTeam <- SATHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

SATHomeTeam <- SATHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))


SATAwayTeam <- SATAwayTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
SATAwayTeam <-  SATAwayTeam %>% mutate( HomeInitl = str_sub(game, start = -3)) #extract home team intl
SATAwayTeam <- left_join(SATAwayTeam, TeamInitlKey, by = c("HomeInitl" = "Initl")) #get home team name

SATAwayTeam <- SATAwayTeam %>% rename("HomeTeam" = "Name", "AwayTeam" = "team")

SATAwayTeam <- SATAwayTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))

#just need the shots from away. the origional has against stats for everything else
SATAwayTeam <- SATAwayTeam %>% select(GameKey, shots) %>% rename(away_shots = shots)

SAT_Data <- merge(SATHomeTeam, SATAwayTeam)
```



```{r}
GoalsAwayTeam <- Goals_Data[grepl("@", Goals_Data$game),]
GoalsHomeTeam <- Goals_Data[!grepl("@", Goals_Data$game),]


GoalsHomeTeam <- GoalsHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
GoalsHomeTeam <-  GoalsHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
GoalsHomeTeam <- left_join(GoalsHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

GoalsHomeTeam <- GoalsHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

GoalsHomeTeam <- GoalsHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))



GoalsAwayTeam <- GoalsAwayTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
GoalsAwayTeam <-  GoalsAwayTeam %>% mutate( HomeInitl = str_sub(game, start = -3)) #extract home team intl
GoalsAwayTeam <- left_join(GoalsAwayTeam, TeamInitlKey, by = c("HomeInitl" = "Initl")) #get home team name

GoalsAwayTeam <- GoalsAwayTeam %>% rename("HomeTeam" = "Name", "AwayTeam" = "team")

GoalsAwayTeam <- GoalsAwayTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))

colnames(GoalsHomeTeam) <- c(paste("Home ", colnames(GoalsHomeTeam)))
names(GoalsHomeTeam)[names(GoalsHomeTeam) == 'Home  GameKey'] <- 'GameKey'

colnames(GoalsAwayTeam) <- c(paste("Away ", colnames(GoalsAwayTeam)))
names(GoalsAwayTeam)[names(GoalsAwayTeam) == 'Away  GameKey'] <- 'GameKey'


MiscAwayTeam <- Misc_Data[grepl("@", Misc_Data$game),]
MiscHomeTeam <- Misc_Data[!grepl("@", Misc_Data$game),]


MiscHomeTeam <- MiscHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
MiscHomeTeam <-  MiscHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
MiscHomeTeam <- left_join(MiscHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

MiscHomeTeam <- MiscHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

MiscHomeTeam <- MiscHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))


colnames(MiscHomeTeam) <- c(paste("Home ", colnames(MiscHomeTeam)))
names(MiscHomeTeam)[names(MiscHomeTeam) == 'Home  GameKey'] <- 'GameKey'



MiscAwayTeam <- MiscAwayTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
MiscAwayTeam <-  MiscAwayTeam %>% mutate( HomeInitl = str_sub(game, start = -3)) #extract home team intl
MiscAwayTeam <- left_join(MiscAwayTeam, TeamInitlKey, by = c("HomeInitl" = "Initl")) #get home team name

MiscAwayTeam <- MiscAwayTeam %>% rename("HomeTeam" = "Name", "AwayTeam" = "team")

MiscAwayTeam <- MiscAwayTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))

colnames(MiscAwayTeam) <- c(paste("Away ", colnames(MiscAwayTeam)))
names(MiscAwayTeam)[names(MiscAwayTeam) == 'Away  GameKey'] <- 'GameKey'


PPAwayTeam <- PP_Data[grepl("@", PP_Data$game),]
PPHomeTeam <- PP_Data[!grepl("@", PP_Data$game),]


PPHomeTeam <- PPHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
PPHomeTeam <-  PPHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
PPHomeTeam <- left_join(PPHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

PPHomeTeam <- PPHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

PPHomeTeam <- PPHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))


colnames(PPHomeTeam) <- c(paste("Home ", colnames(PPHomeTeam)))
names(PPHomeTeam)[names(PPHomeTeam) == 'Home  GameKey'] <- 'GameKey'



PPAwayTeam <- PPAwayTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
PPAwayTeam <-  PPAwayTeam %>% mutate( HomeInitl = str_sub(game, start = -3)) #extract home team intl
PPAwayTeam <- left_join(PPAwayTeam, TeamInitlKey, by = c("HomeInitl" = "Initl")) #get home team name

PPAwayTeam <- PPAwayTeam %>% rename("HomeTeam" = "Name", "AwayTeam" = "team")

PPAwayTeam <- PPAwayTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))

colnames(PPAwayTeam) <- c(paste("Away ", colnames(PPAwayTeam)))
names(PPAwayTeam)[names(PPAwayTeam) == 'Away  GameKey'] <- 'GameKey'


GameDataJoined <- merge(FO_Data, SAT_Data, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, GoalsAwayTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, GoalsHomeTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, MiscAwayTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, MiscHomeTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, PPAwayTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, PPHomeTeam, by.x = "GameKey", by.y = "GameKey")
```

```{r}
#remove duplicate columns and unneeded and rename
GameDataJoined_Cleaned <- GameDataJoined %>% select(-index.x, -index.y, -gp.x, -gp.y, -game.x, -HomeTeam.y, -game.y, -Date.y, -AwayInitl.y, -AwayTeam.y, -`Away  index.x`, -`Away  AwayTeam.x`, -`Away  game.x`, -`Away  gp.x`, -`Away  Date.x`, -`Away  HomeInitl.x`, -`Away  HomeTeam.x`, -`Home  index.x`, -`Home  HomeTeam.x`, -`Home  game.x`, -`Home  gp.x`, -`Home  Date.x`, -`Home  AwayInitl.x`, -`Home  AwayTeam.x`, -`Away  index.y`, -`Away  AwayTeam.y`, -`Away  game.y`, -`Away  gp.y`, -`Away  Date.y`, -`Away  HomeInitl.y`, -`Away  HomeTeam.y`, -`Home  index.y`, -`Home  HomeTeam.y`, -`Home  game.y`, -`Home  gp.y`, -`Home  Date.y`, -`Home  AwayInitl.y`, -`Home  AwayTeam.y`, -`Away  AwayTeam`, -`Away  game`, -`Away  gp`, -`Away  Date`, -`Away  HomeInitl`, -`Away  HomeTeam`, -`Home  index`, -`Home  HomeTeam`, -`Home  game`, -`Home  gp`, -`Home  Date`, -`Home  AwayInitl`, -`Home  AwayTeam`, -`Away  index`) %>% rename(HomeTeam = HomeTeam.x, Date = Date.x, AwayInitl = AwayInitl.x, AwayTeam = AwayTeam.x)
```



```{r}
#make season designation
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% mutate(Season = case_when( month(Date) >= 6 ~ paste(year(Date), "-", year(Date) + 1)
                                                                                ,month(Date) < 6 ~ paste(year(Date) - 1, "-", year(Date))
))

GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% arrange(Date)

#convert number format
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>%
    mutate_at(vars(c(3:24, 28:81, 83:93, 95:115, 117:132, 134:139)),list(~as.numeric(str_replace_all(.,'--','0'))))

```

```{r}
#Get per game points per game


TeamGamePPG <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameDataJoined_Cleaned$Season)) {
    
    
   teamseason <- GameDataJoined_Cleaned %>% filter(Season == season) %>% filter(HomeTeam == team | AwayTeam == team)
   
   teamseason <- teamseason %>% mutate(GameNumber = row_number(), FocusTeam = team) %>% relocate(FocusTeam, GameNumber)

   teamseason <- teamseason %>% mutate(Points = case_when(FocusTeam == HomeTeam ~ `Home  p`
                                            ,FocusTeam == AwayTeam ~ `Away  p`)) %>% select(Season, FocusTeam, GameNumber, GameKey, Points)
   
   
   teamseason <- teamseason %>% mutate(TotalPoints = cumsum(Points), PPG = TotalPoints/GameNumber)
   
   teamseason <- teamseason %>% mutate(PPG_prior = lag(PPG)) %>% replace(is.na(.), 0)
   
   TeamGamePPG <- rbind(TeamGamePPG, teamseason)
   
  }
}

```

```{r}
#Create OT field - what we are tryingto predict
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% mutate(OT = case_when(`Home  ot`+`Away  ot` == 0 ~ 0
                                                 ,`Home  ot`+`Away  ot` != 0 ~ 1))

#Attach PPG and Organize
#Remember: PPG is what it was after the game. Need to get what it was after the game before

GameData_PPG <- merge(GameDataJoined_Cleaned, TeamGamePPG, by.x = c("HomeTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% rename(HomeGameNumber = GameNumber, HomePoints_post = Points, HomeTotalPoints_post = TotalPoints, HomePPG_post = PPG, HomePPG_prior = PPG_prior) %>% rename(Season = Season.x) %>% select(-Season.y)


GameData_PPG <- merge(GameData_PPG, TeamGamePPG, by.x = c("AwayTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% rename(AwayGameNumber = GameNumber, AwayPoints_post = Points, AwayTotalPoints_post = TotalPoints, AwayPPG_post = PPG, AwayPPG_prior = PPG_prior) %>% rename(Season = Season.x) %>% select(-Season.y)


GameData_PPG <- GameData_PPG %>% mutate(PPG_Diff_ABS = abs(HomePPG_prior - AwayPPG_prior)
                                        ,PPG_Diff = HomePPG_prior - AwayPPG_prior)

```


```{r}
#Get GA per game and GAA


TeamGameGAA <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameDataJoined_Cleaned$Season)) {
    
    
   teamseason <- GameDataJoined_Cleaned %>% filter(Season == season) %>% filter(HomeTeam == team | AwayTeam == team)
   
   teamseason <- teamseason %>% mutate(GameNumber = row_number(), FocusTeam = team) %>% 
     mutate(OtherTeam = if_else(FocusTeam == HomeTeam, AwayTeam, HomeTeam)) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam)

   teamseason <- teamseason %>% mutate(GA = case_when(FocusTeam == HomeTeam ~ `Home  ga`
                                            ,FocusTeam == AwayTeam ~ `Away  ga`)) %>% 
     mutate(GF = case_when(FocusTeam == HomeTeam ~ `Home  gf`
                                            ,FocusTeam == AwayTeam ~ `Away  gf`)) %>% 
     select(Season, FocusTeam, GameNumber, OtherTeam, GameKey, GF, GA)
   
   
   teamseason <- teamseason %>% mutate(GA_limited = if_else(GA > 5, 5, GA)) %>% 
     mutate(GAA = cumsum(GA_limited) / GameNumber) #this is after the given game
   
   
   teamseason <- teamseason %>% mutate(GAA_prior = lag(GAA)) %>% replace(is.na(.), 0)
   
   TeamGameGAA <- rbind(TeamGameGAA, teamseason)
   
  }
}


#join other team's stats to compare GF to other team's GAA

TeamGameGAA_compare <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameDataJoined_Cleaned$Season)) {
    
    
   teamseason <- TeamGameGAA %>% filter(Season == season) %>% filter(FocusTeam == team)
   
   teamseason <- merge(teamseason, TeamGameGAA, by.x = c("OtherTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% rename(Season = Season.x, GameNumber = GameNumber.x, GF = GF.x, GA = GA.x, GA_limited = GA_limited.x, GAA = GAA.x, GAA_prior = GAA_prior.x, GameNumber_other = GameNumber.y, GF_other = GF.y, GA_other = GA.y, GA_limited_other = GA_limited.y, GAA_other = GAA.y, GAA_prior_other = GAA_prior.y) %>%
     select(-Season.y, -OtherTeam.y) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam) %>% 
     arrange(GameNumber)
   

   teamseason <- teamseason %>% mutate(Goals_Above_GAA = GF - GAA_prior_other) 
   
   
   teamseason <- teamseason %>% mutate(Average_Goals_Above_GAA = cumsum(Goals_Above_GAA) / GameNumber) #this is after the given game
   
   
   teamseason <- teamseason %>% mutate(Average_Goals_Above_GAA_prior = lag(Average_Goals_Above_GAA)) %>% replace(is.na(.), 0)
   
   TeamGameGAA_compare <- rbind(TeamGameGAA_compare, teamseason)
   
  }
}



#Attach
GameData_PPG_GAA <- merge(GameData_PPG, TeamGameGAA_compare, by.x = c("HomeTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(Season = Season.x, Home_Average_Goals_Above_GAA_prior = Average_Goals_Above_GAA_prior, HomeGAA_prior = GAA_prior,) %>% 
  select(-Season.y, -GF, -GA, -GA_limited, -GAA, -GameNumber_other, -GF_other, -GA_other, -GA_limited_other, -GAA_other, -GAA_prior_other, -Goals_Above_GAA, -Average_Goals_Above_GAA, -GameNumber, -OtherTeam)



GameData_PPG_GAA <- merge(GameData_PPG_GAA, TeamGameGAA_compare, by.x = c("AwayTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(Season = Season.x, Away_Average_Goals_Above_GAA_prior = Average_Goals_Above_GAA_prior, AwayGAA_prior = GAA_prior,) %>% 
  select(-Season.y, -GF, -GA, -GA_limited, -GAA, -GameNumber_other, -GF_other, -GA_other, -GA_limited_other, -GAA_other, -GAA_prior_other, -Goals_Above_GAA, -Average_Goals_Above_GAA, -GameNumber, -OtherTeam)

GameData_PPG_GAA <- GameData_PPG_GAA %>% mutate(HomeExpectedGoals = Home_Average_Goals_Above_GAA_prior + AwayGAA_prior,
                            AwayExpectedGoals = Away_Average_Goals_Above_GAA_prior + HomeGAA_prior,)

GameData_PPG_GAA <- GameData_PPG_GAA %>% mutate(Expected_Goals_Diff_ABS = abs(HomeExpectedGoals - AwayExpectedGoals)
                                                ,Expected_Goals_Diff = HomeExpectedGoals - AwayExpectedGoals)

```

Weighted USAT
```{r}
#Get USAT per game and PPG


TeamGameUSAT <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameData_PPG_GAA$Season)) {
    
    
   teamseason <- GameData_PPG_GAA %>% filter(Season == season) %>% filter(HomeTeam == team | AwayTeam == team) %>% arrange(Date)
   
   teamseason <- teamseason %>% mutate(GameNumber = row_number(), FocusTeam = team) %>% 
     mutate(OtherTeam = if_else(FocusTeam == HomeTeam, AwayTeam, HomeTeam)) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam)

   teamseason <- teamseason %>% mutate(PPG_post = case_when(FocusTeam == HomeTeam ~ HomePPG_post
                                            ,FocusTeam == AwayTeam ~ AwayPPG_post)) %>% 
     mutate(PPG_prior = case_when(FocusTeam == HomeTeam ~ HomePPG_prior
                                            ,FocusTeam == AwayTeam ~ AwayPPG_prior)) %>% 
     mutate(USAT = case_when(FocusTeam == HomeTeam ~ usat
                                            ,FocusTeam == AwayTeam ~ -usat)) %>% 
     select(Season, FocusTeam, GameNumber, OtherTeam, GameKey, PPG_post, PPG_prior, USAT)
   
  
   
   TeamGameUSAT <- rbind(TeamGameUSAT, teamseason)
   
  }
}


#join other team's stats to compare GF to other team's GAA

TeamGameUSAT_compare <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameDataJoined_Cleaned$Season)) {
    
    
   teamseason <- TeamGameUSAT %>% filter(Season == season) %>% filter(FocusTeam == team)
   
   teamseason <- merge(teamseason, TeamGameUSAT, by.x = c("OtherTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% rename(Season = Season.x, GameNumber = GameNumber.x, PPG_post = PPG_post.x, PPG_prior = PPG_prior.x, USAT = USAT.x, GameNumber_other = GameNumber.y, PPG_post_other = PPG_post.y, PPG_prior_other = PPG_prior.y, USAT_other = USAT.y) %>%
     select(-Season.y, -OtherTeam.y) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam) %>% 
     arrange(GameNumber)
   

   teamseason <- teamseason %>% mutate(WeightingFactor = (PPG_prior - PPG_prior_other) / 2) 
   
   teamseason <- teamseason %>% mutate(USAT_weighted = 
                 case_when(WeightingFactor > 0 ~ 
                                      case_when( USAT > 0 ~ USAT - (USAT * WeightingFactor)
                                                ,USAT < 0 ~ USAT - abs(USAT * WeightingFactor)
                                                ,USAT == 0 ~ 0
                                               )
                          ,WeightingFactor < 0 ~ 
                                      case_when( USAT > 0 ~ USAT + (USAT * WeightingFactor)
                                                ,USAT < 0 ~ USAT + abs(USAT * WeightingFactor)
                                                ,USAT == 0 ~ 0
                                               )
                          ,WeightingFactor == 0 ~ USAT
                           ))
   
   teamseason <- teamseason %>% mutate(USAT_weighted_earlylimit = if_else(GameNumber <= 5, USAT, USAT_weighted))
   
   
   teamseason <- teamseason %>% mutate(Average_USAT_weighted = cumsum(USAT_weighted_earlylimit) / GameNumber) #this is after the given game
   
   
   teamseason <- teamseason %>% mutate(Average_USAT_weighted_prior = lag(Average_USAT_weighted)) %>% replace(is.na(.), 0)
   
   TeamGameUSAT_compare <- rbind(TeamGameUSAT_compare, teamseason)
   
  }
}

TeamGameUSAT_compare <- TeamGameUSAT_compare %>% select(FocusTeam, GameKey, Average_USAT_weighted_prior)


#Attach
GameData_PPG_GAA_SAT <- merge(GameData_PPG_GAA, TeamGameUSAT_compare, by.x = c("HomeTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(Home_Average_USAT_weighted_prior = Average_USAT_weighted_prior)



GameData_PPG_GAA_SAT <- merge(GameData_PPG_GAA_SAT, TeamGameUSAT_compare, by.x = c("AwayTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(Away_Average_USAT_weighted_prior = Average_USAT_weighted_prior)



GameData_PPG_GAA_SAT <- GameData_PPG_GAA_SAT %>% mutate(USAT_weighted_Diff_ABS = abs(Home_Average_USAT_weighted_prior - Away_Average_USAT_weighted_prior)
                                                        ,USAT_weighted_Diff = Home_Average_USAT_weighted_prior - Away_Average_USAT_weighted_prior)
```

```{r}
#Get USAT per game and PPG


TeamGameFO <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameData_PPG_GAA_SAT$Season)) {
    
    
   teamseason <- GameData_PPG_GAA_SAT %>% filter(Season == season) %>% filter(HomeTeam == team | AwayTeam == team) %>% arrange(Date)
   
   teamseason <- teamseason %>% mutate(GameNumber = row_number(), FocusTeam = team) %>% 
     mutate(OtherTeam = if_else(FocusTeam == HomeTeam, AwayTeam, HomeTeam)) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam)

   teamseason <- teamseason %>% mutate(PPG_post = case_when(FocusTeam == HomeTeam ~ HomePPG_post
                                            ,FocusTeam == AwayTeam ~ AwayPPG_post)) %>% 
     mutate(PPG_prior = case_when(FocusTeam == HomeTeam ~ HomePPG_prior
                                            ,FocusTeam == AwayTeam ~ AwayPPG_prior)) %>% 
     mutate(FOP = case_when(FocusTeam == HomeTeam ~ `fow%`
                                            ,FocusTeam == AwayTeam ~ 100 - `fow%`)) %>% 
     select(Season, FocusTeam, GameNumber, OtherTeam, GameKey, PPG_post, PPG_prior, FOP)
   
  
   
   TeamGameFO <- rbind(TeamGameFO, teamseason)
   
  }
}


#join other team's stats to compare GF to other team's GAA

TeamGameFO_compare <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameDataJoined_Cleaned$Season)) {
    
    
   teamseason <- TeamGameFO %>% filter(Season == season) %>% filter(FocusTeam == team)
   
   teamseason <- merge(teamseason, TeamGameFO, by.x = c("OtherTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% rename(Season = Season.x, GameNumber = GameNumber.x, PPG_post = PPG_post.x, PPG_prior = PPG_prior.x, FOP = FOP.x, GameNumber_other = GameNumber.y, PPG_post_other = PPG_post.y, PPG_prior_other = PPG_prior.y, FOP_other = FOP.y) %>%
     select(-Season.y, -OtherTeam.y) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam) %>% 
     arrange(GameNumber)
   

   teamseason <- teamseason %>% mutate(WeightingFactor = (PPG_prior - PPG_prior_other) / 2) 
   
   teamseason <- teamseason %>% mutate(FOP_weighted = #adjusting % by 10 at max
                 case_when(WeightingFactor > 0 ~ 
                                      case_when( FOP > 50 ~ FOP - ((FOP-50) * WeightingFactor) 
                                                ,FOP < 50 ~ FOP - abs((50-FOP) * WeightingFactor)
                                                ,FOP == 50 ~ 50
                                               )
                          ,WeightingFactor < 0 ~ 
                                      case_when( FOP > 50 ~ FOP + ((FOP-50) * WeightingFactor)
                                                ,FOP < 50 ~ FOP + abs((50-FOP) * WeightingFactor)
                                                ,FOP == 50 ~ 50
                                               )
                          ,WeightingFactor == 0 ~ FOP
                           ))
   
   teamseason <- teamseason %>% mutate(FOP_weighted_earlylimit = if_else(GameNumber <= 5, FOP, FOP_weighted))
   
   teamseason <- teamseason %>% mutate(FOP_weighted_earlylimit = case_when(
     FOP_weighted_earlylimit > 60 ~ 60, 
     FOP_weighted_earlylimit < 40 ~ 40,
     FOP_weighted_earlylimit <= 60 & FOP_weighted_earlylimit >= 40 ~ FOP_weighted_earlylimit))
   
   
   teamseason <- teamseason %>% mutate(Average_FOP_weighted = cumsum(FOP_weighted_earlylimit) / GameNumber) #this is after the given game
   
   
   teamseason <- teamseason %>% mutate(Average_FOP_weighted_prior = lag(Average_FOP_weighted)) %>% replace(is.na(.), 0)
   
   TeamGameFO_compare <- rbind(TeamGameFO_compare, teamseason)
   
  }
}

TeamGameFO_compare <- TeamGameFO_compare %>% select(FocusTeam, GameKey, Average_FOP_weighted_prior)


#Attach
GameData_PPG_GAA_SAT_FOP <- merge(GameData_PPG_GAA_SAT, TeamGameFO_compare, by.x = c("HomeTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(Home_Average_FOP_weighted_prior = Average_FOP_weighted_prior)



GameData_PPG_GAA_SAT_FOP <- merge(GameData_PPG_GAA_SAT_FOP, TeamGameFO_compare, by.x = c("AwayTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(Away_Average_FOP_weighted_prior = Average_FOP_weighted_prior)



GameData_PPG_GAA_SAT_FOP <- GameData_PPG_GAA_SAT_FOP %>% mutate(FOP_weighted_Diff_ABS = abs(Home_Average_FOP_weighted_prior - Away_Average_FOP_weighted_prior)
                                                                ,FOP_weighted_Diff = Home_Average_FOP_weighted_prior - Away_Average_FOP_weighted_prior)
```

Power Play vs Penalty Kill

(PP%_home - PK%_away) - (PP%_away - PK%_home) = Special Teams Value (STV)


```{r}
#Get PP count, successes, PP given, and PK per game


TeamGameSTV <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameData_PPG_GAA_SAT_FOP$Season)) {
    
    
   teamseason <- GameData_PPG_GAA_SAT_FOP %>% filter(Season == season) %>% filter(HomeTeam == team | AwayTeam == team) %>% arrange(Date)
   
   teamseason <- teamseason %>% mutate(GameNumber = row_number(), FocusTeam = team) %>% 
     mutate(OtherTeam = if_else(FocusTeam == HomeTeam, AwayTeam, HomeTeam)) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam)

   teamseason <- teamseason %>% mutate(PP_Opp = case_when(FocusTeam == HomeTeam ~ `Home  PP Opp`
                                            ,FocusTeam == AwayTeam ~ `Away  PP Opp`)) %>% 
     mutate(PP_G = case_when(FocusTeam == HomeTeam ~ `Home  PP GF`
                                            ,FocusTeam == AwayTeam ~ `Away  PP GF`)) %>% 
     mutate(PK_Opp = case_when(FocusTeam == HomeTeam ~ `Away  PP Opp`
                                            ,FocusTeam == AwayTeam ~ `Home  PP Opp`)) %>% 
     mutate(PK_Success = case_when(FocusTeam == HomeTeam ~ `Away  PP Opp` - `Away  PP GF`
                                            ,FocusTeam == AwayTeam ~ `Home  PP Opp` - `Home  PP GF`)) %>%
     mutate(PP_Opp_total = cumsum(PP_Opp), PP_G_total = cumsum(PP_G), PK_Opp_total = cumsum(PK_Opp), PK_Success_total = cumsum(PK_Success)) %>% 
     select(Season, FocusTeam, GameNumber, OtherTeam, GameKey, PP_Opp, PP_G, PK_Opp, PK_Success, PP_Opp_total, PP_G_total, PK_Opp_total, PK_Success_total)
   
  
   teamseason <- teamseason %>% mutate(`PP%_post` = PP_G_total / PP_Opp_total,
                         `PK%_post` = PK_Success_total / PK_Opp_total) %>% 
     mutate(`PP%_prior` = lag(`PP%_post`),
            `PK%_prior` = lag(`PK%_post`))
   
   
   TeamGameSTV <- rbind(TeamGameSTV, teamseason)
   
  }
}

#simplfy to stats we need
TeamGameSTV <- TeamGameSTV %>% select(FocusTeam, GameNumber, GameKey, OtherTeam, `PP%_prior`, `PK%_prior`)





#Attach
GameData_PPG_GAA_SAT_FOP_STV <- merge(GameData_PPG_GAA_SAT_FOP, TeamGameSTV, by.x = c("HomeTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(`HomePP%_prior` = `PP%_prior`,
         `HomePK%_prior` = `PK%_prior`)



GameData_PPG_GAA_SAT_FOP_STV <- merge(GameData_PPG_GAA_SAT_FOP_STV, TeamGameSTV, by.x = c("AwayTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(`AwayPP%_prior` = `PP%_prior`,
         `AwayPK%_prior` = `PK%_prior`)



GameData_PPG_GAA_SAT_FOP_STV <- GameData_PPG_GAA_SAT_FOP_STV %>% mutate(SpecialTeamsValue_ABS = abs((`HomePP%_prior` - `AwayPK%_prior`) - (`AwayPP%_prior` - `HomePK%_prior`))
                                                                        , SpecialTeamsValue = (`HomePP%_prior` - `AwayPK%_prior`) - (`AwayPP%_prior` - `HomePK%_prior`))
```


Frequency of OT

Total OT/Games - (home OT + Away OT) / (Home Games + Away Games)

```{r}
TeamGameOT <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameData_PPG_GAA_SAT_FOP_STV$Season)) {
    
    
   teamseason <- GameData_PPG_GAA_SAT_FOP_STV %>% filter(Season == season) %>% filter(HomeTeam == team | AwayTeam == team) %>% arrange(Date)
   
   teamseason <- teamseason %>% mutate(GameNumber = row_number(), FocusTeam = team) %>% 
     mutate(OtherTeam = if_else(FocusTeam == HomeTeam, AwayTeam, HomeTeam)) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam)

   teamseason <- teamseason %>% 
     select(Season, FocusTeam, GameNumber, OtherTeam, GameKey, OT)
   
  teamseason <- teamseason %>% mutate(OT_total = cumsum(OT)) %>% 
    mutate(OT_total_prior = lag(OT_total))
   
   
   
   TeamGameOT <- rbind(TeamGameOT, teamseason)
   
  }
}

#simplfy to stats we need
TeamGameOT <- TeamGameOT %>% select(FocusTeam, GameKey, OT_total_prior)

#Attach
GameData_PPG_GAA_SAT_FOP_STV_OT <- merge(GameData_PPG_GAA_SAT_FOP_STV, TeamGameOT, by.x = c("HomeTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(HomeOT_total_prior = OT_total_prior)



GameData_PPG_GAA_SAT_FOP_STV_OT <- merge(GameData_PPG_GAA_SAT_FOP_STV_OT, TeamGameOT, by.x = c("AwayTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(AwayOT_total_prior = OT_total_prior)



GameData_PPG_GAA_SAT_FOP_STV_OT <- GameData_PPG_GAA_SAT_FOP_STV_OT %>% mutate(OTperGame = abs((HomeOT_total_prior + AwayOT_total_prior) / ((HomeGameNumber - 1) + (AwayGameNumber - 1))))


```


Active Team Salary

See Scrape Players and Salaries for all the work that went into this
```{r}
load("ContractDifferences_2024.RData")

#Normalize Formatting on GameKey
GameData_PPG_GAA_SAT_FOP_STV_OT <- GameData_PPG_GAA_SAT_FOP_STV_OT %>% mutate(GameKey = str_squish(GameKey))

ContractDifferences <- ContractDifferences_2024 %>% mutate(GameKey = str_squish(GameKeyBeta)) %>% select(-GameKeyBeta)

#Montreal has an accent
library(stringi)
GameData_PPG_GAA_SAT_FOP_STV_OT <- GameData_PPG_GAA_SAT_FOP_STV_OT %>% mutate(GameKey = stri_trans_general(str = GameKey, id = "Latin-ASCII"))

ContractDifferences <- ContractDifferences %>% mutate(GameKey = stri_trans_general(str = GameKey, id = "Latin-ASCII"))


#Join
GameData_PPG_GAA_SAT_FOP_STV_OT_CT <- left_join(GameData_PPG_GAA_SAT_FOP_STV_OT, ContractDifferences, by = c("GameKey" = "GameKey"))

#Test for NA
GameData_PPG_GAA_SAT_FOP_STV_OT_CT %>% filter(is.na(ContractDifference_ABS))

```


#Identify Divisional/Conference Matchups
```{r}
Divisions_2024 <- data.frame(Name = c("Boston Bruins", "Buffalo Sabres", "Detroit Red Wings", "Florida Panthers", "Montréal Canadiens", "Ottawa Senators", "Tampa Bay Lightning", "Toronto Maple Leafs",
                                              "Carolina Hurricanes", "Columbus Blue Jackets", "New Jersey Devils", "New York Islanders", "New York Rangers", "Philadelphia Flyers", "Pittsburgh Penguins", "Washington Capitals",
                                              "Utah Hockey Club", "Chicago Blackhawks", "Colorado Avalanche", "Dallas Stars", "Minnesota Wild", "Nashville Predators", "St. Louis Blues", "Winnipeg Jets",
                                              "Anaheim Ducks", "Calgary Flames", "Edmonton Oilers", "Los Angeles Kings", "San Jose Sharks", "Seattle Kraken", "Vancouver Canucks", "Vegas Golden Knights")
                                     ,Conference = c(rep("Eastern", 16), rep("Western", 16))
                                     ,Division = c(rep("Atlantic", 8), rep("Metropolitan", 8), rep("Central", 8), rep("Pacific", 8))
                                     )



DivisionData_2024 <- GameData_PPG_GAA_SAT_FOP_STV_OT_CT %>% #filter(Season %in% c("2021 - 2022", "2022 - 2023", "2023 - 2024")) %>% 
  left_join(Divisions_2024, by = join_by("AwayTeam" == "Name")) %>% rename(Away_Conference = Conference, Away_Division = Division) %>% 
  left_join(Divisions_2024, by = join_by("HomeTeam" == "Name")) %>% rename(Home_Conference = Conference, Home_Division = Division) %>% 
  mutate(DivisionMatchup = if_else(Away_Division == Home_Division, 1, 0), ConferenceMatchup = if_else(Away_Conference == Home_Conference, 1, 0))

#GameData_Divisions <- rbind(DivisionData_2014_to_2016, DivisionData_2017_to_2019, DivisionData_2020, DivisionData_2021_to_2024)

GameData_Divisions <- DivisionData_2024

```


Points Away From Playoffs

-Need current standings for every game

```{r}
#TeamGameOT <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"

#i <- 1

#n <- 1

#Divisions and other things were weird in COVID Year. Removing to get rid of noise
GameData_Divisions <- GameData_Divisions %>% filter(Season != "2020 - 2021")

GameData_Divisions <- GameData_Divisions %>% mutate(Home_PointsFromPlayoffs = NA, Away_PointsFromPlayoffs = NA)


for (i in 1:nrow(GameData_Divisions)) {
  
  tryCatch({
  
  #Get most recent game for each team
  GamesInSeasonSoFar <- GameData_Divisions %>% filter(Season == GameData_Divisions[i,"Season"], Date < GameData_Divisions[i,"Date"])
  
  HomeGameMaxDate <- GamesInSeasonSoFar %>% group_by(HomeTeam) %>% summarise(MaxDateHome = max(Date))
  
  AwayGameMaxDate <- GamesInSeasonSoFar %>% group_by(AwayTeam) %>% summarise(MaxDateAway = max(Date))
  
  TeamsAndDates <- left_join(HomeGameMaxDate, AwayGameMaxDate , by = join_by(HomeTeam == AwayTeam)) %>% 
    mutate(MostRecentHomeOrAway = if_else(MaxDateHome > MaxDateAway, "Home", "Away")) 
   
  HomeTeamsAndDates <- TeamsAndDates %>% filter(MostRecentHomeOrAway == "Home")
  
  AwayTeamsAndDates <- TeamsAndDates %>% filter(MostRecentHomeOrAway == "Away") %>% rename(AwayTeam = HomeTeam)
  
  HomeTeamsAndDates <- HomeTeamsAndDates %>% mutate(Points = NA, Conference = NA, Division = NA)
  
  for (n in 1:nrow(HomeTeamsAndDates)) {
   HomeTeamsAndDates$Points[n] <- GamesInSeasonSoFar %>% filter(HomeTeam == HomeTeamsAndDates$HomeTeam[n], Date == HomeTeamsAndDates$MaxDateHome[n]) %>% select(Points = HomeTotalPoints_post) %>% as.numeric()
   
   HomeTeamsAndDates$Conference[n] <- GamesInSeasonSoFar %>% filter(HomeTeam == HomeTeamsAndDates$HomeTeam[n], Date == HomeTeamsAndDates$MaxDateHome[n]) %>% select(Conference = Home_Conference) %>% as.character()
   
   HomeTeamsAndDates$Division[n] <- GamesInSeasonSoFar %>% filter(HomeTeam == HomeTeamsAndDates$HomeTeam[n], Date == HomeTeamsAndDates$MaxDateHome[n]) %>% select(Division = Home_Division) %>% as.character()
   
  }

  AwayTeamsAndDates <- AwayTeamsAndDates %>% mutate(Points = NA, Conference = NA, Division = NA)
  
  for (n in 1:nrow(AwayTeamsAndDates)) {
   AwayTeamsAndDates$Points[n] <- GamesInSeasonSoFar %>% filter(AwayTeam == AwayTeamsAndDates$AwayTeam[n], Date == AwayTeamsAndDates$MaxDateAway[n]) %>% select(Points = AwayTotalPoints_post) %>% as.numeric()
   
   AwayTeamsAndDates$Conference[n] <- GamesInSeasonSoFar %>% filter(AwayTeam == AwayTeamsAndDates$AwayTeam[n], Date == AwayTeamsAndDates$MaxDateAway[n]) %>% select(Conference = Away_Conference) %>% as.character()
   
   AwayTeamsAndDates$Division[n] <- GamesInSeasonSoFar %>% filter(AwayTeam == AwayTeamsAndDates$AwayTeam[n], Date == AwayTeamsAndDates$MaxDateAway[n]) %>% select(Division = Away_Division) %>% as.character()
   
  }
  
  
  
  CurrentStandings <- rbind(
  AwayTeamsAndDates %>% rename(Team = AwayTeam) %>% select(Team, Points, Conference, Division)
  
  ,HomeTeamsAndDates %>% rename(Team = HomeTeam) %>% select(Team, Points, Conference, Division)
  )
  
  
  #Get the home and away teams and determine how far they are from a playoff spot
  
  HomeTeam <- GameData_Divisions[i,"HomeTeam"]
  
  HomeConference <- GameData_Divisions[i,"Home_Conference"]
  
  HomeDivision <- GameData_Divisions[i,"Home_Division"]
  
  HomeDivsionPlayoffTeams <- CurrentStandings %>% filter(Division == HomeDivision) %>% slice_max(Points, n = 3, with_ties = FALSE)
  
  HomeOtherDivsionPlayoffTeams <- CurrentStandings %>% filter(Conference == HomeConference, Division != HomeDivision) %>% slice_max(Points, n = 3, with_ties = FALSE)
  
  HomeWildcardTeams <- CurrentStandings %>% filter(Conference == HomeConference, !Team %in% HomeDivsionPlayoffTeams$Team, !Team %in% HomeOtherDivsionPlayoffTeams$Team) %>% slice_max(Points, n = 2, with_ties = FALSE)
  
  HomePlayoffPointsCuttoff <- min(HomeDivsionPlayoffTeams$Points, HomeWildcardTeams$Points)
  
  AwayTeam <- GameData_Divisions[i,"AwayTeam"]
  
  AwayConference <- GameData_Divisions[i,"Away_Conference"]
  
  AwayDivision <- GameData_Divisions[i,"Away_Division"]
  
  AwayDivsionPlayoffTeams <- CurrentStandings %>% filter(Division == AwayDivision) %>% slice_max(Points, n = 3, with_ties = FALSE)
  
  AwayOtherDivsionPlayoffTeams <- CurrentStandings %>% filter(Conference == AwayConference, Division != AwayDivision) %>% slice_max(Points, n = 3, with_ties = FALSE)
  
  AwayWildcardTeams <- CurrentStandings %>% filter(Conference == AwayConference, !Team %in% AwayDivsionPlayoffTeams$Team, !Team %in% AwayOtherDivsionPlayoffTeams$Team) %>% slice_max(Points, n = 2, with_ties = FALSE)
  
  
  AwayPlayoffPointsCuttoff <- min(AwayDivsionPlayoffTeams$Points, AwayWildcardTeams$Points)
  
  
  
  HomePoints <- GameData_Divisions[i,"HomePPG_prior"] * (GameData_Divisions[i, "HomeGameNumber"] - 1)
  
  AwayPoints <- GameData_Divisions[i,"AwayPPG_prior"] * (GameData_Divisions[i, "AwayGameNumber"] - 1)
  
  GameData_Divisions[i, "Home_PointsFromPlayoffs"] <- HomePlayoffPointsCuttoff - HomePoints
  
  GameData_Divisions[i, "Away_PointsFromPlayoffs"] <- AwayPlayoffPointsCuttoff - AwayPoints
  
  
  }, error=function(e){})
  
}
```






Games in the last weeks, average hits per game, shot block %, streak
```{r}

TeamGame_stats <- data.frame()


#team <- "Boston Bruins"
#season <- "2017 - 2018"


for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameData_Divisions$Season)) {
    
    
   teamseason <- GameData_Divisions %>% filter(Season == season) %>% filter(HomeTeam == team | AwayTeam == team) %>% arrange(Date)
   
   if (nrow(teamseason) != 0) {
     
   
   
   teamseason <- teamseason %>% mutate(GameNumber = row_number(), FocusTeam = team) %>% 
     mutate(OtherTeam = if_else(FocusTeam == HomeTeam, AwayTeam, HomeTeam)) %>% 
     relocate(FocusTeam, GameNumber, OtherTeam)

   
   #winning streak -- found here: https://www.r-bloggers.com/2020/06/detecting-streaks-in-r/
  StreakTable <- teamseason %>% mutate(W = case_when(FocusTeam == HomeTeam ~ `Home  w`
                                                     ,FocusTeam == AwayTeam ~ `Away  w`)
                                       ,L = case_when(FocusTeam == HomeTeam ~ `Home  l`
                                                     ,FocusTeam == AwayTeam ~ `Away  l`)
                                       ,OT = case_when(FocusTeam == HomeTeam ~ `Home  ot`
                                                     ,FocusTeam == AwayTeam ~ `Away  ot`)
                                       ) %>% 
    select(W,L,OT) %>% mutate(lagged=lag(W)) %>% #note: that's dplyr::lag, not stats::lag
    mutate(start=(W != lagged))
  StreakTable[1, "start"] <- TRUE
  StreakTable <- StreakTable %>% mutate(streak_id=cumsum(start))
  StreakTable <- StreakTable %>% group_by(streak_id) %>% mutate(streak=row_number()) %>%
    ungroup()
  #new part to make it negative for losing streak
  StreakTable <- StreakTable %>% mutate(streakvalue = case_when(W == 0 ~ -streak,
                                                   W == 1 ~ streak))
  StreakTable <- StreakTable %>% mutate(streakvalue_prior = lag(streakvalue))


   
   
   teamseason <- teamseason %>% mutate(Hits_Diff = case_when(FocusTeam == HomeTeam ~ `Home  Hits` - `Away  Hits`
                                            ,FocusTeam == AwayTeam ~ `Away  Hits` - `Home  Hits`),
                         Shots_Against = case_when(FocusTeam == HomeTeam ~ sat_against
                                            ,FocusTeam == AwayTeam ~ sat_for),
                         Blocked_Shots = case_when(FocusTeam == HomeTeam ~ `Home  Bks`
                                            ,FocusTeam == AwayTeam ~ `Away  Bks`),
                         Blocked_Percent = Blocked_Shots/Shots_Against
                         ) %>% 
     select(FocusTeam, GameNumber, OtherTeam, GameKey, Date, Hits_Diff, Shots_Against, Blocked_Shots,Blocked_Percent)
                         
      teamseason <- teamseason %>% mutate(GamesinLast7Days = NA)
   
   #gamenumber <- 20    
      
      
               
   for (gamenumber in 1:nrow(teamseason)) {
     
  CompareDate <- teamseason %>% filter(GameNumber == gamenumber) %>% pull(Date)
  
  GamesinLast7Days_value <- teamseason %>% filter(CompareDate - Date <= 7 & CompareDate - Date > 0) %>% summarise(Games = n()) %>% pull(Games)
  

  
  teamseason[gamenumber,]$GamesinLast7Days <- GamesinLast7Days_value
     
     }                      
   
   teamseason <- teamseason %>% mutate(Blocked_Percent_post =  cumsum(Blocked_Shots) / cumsum(Shots_Against)
                                       ,Hits_Diff_Avg_post = cumsum(Hits_Diff) / GameNumber
                                       ,Blocked_Percent_prior = lag(Blocked_Percent_post)
                                       ,Hits_Diff_Avg_prior = lag(Hits_Diff_Avg_post))
      
      
  teamseason <- cbind(teamseason, StreakTable %>% select(streakvalue_prior))
   
   
   TeamGame_stats <- rbind(TeamGame_stats, teamseason)
   
   }
  }
}

TeamGame_stats <- TeamGame_stats %>% select(FocusTeam, GameKey, GamesinLast7Days, Blocked_Percent_prior, Hits_Diff_Avg_prior, streakvalue_prior)


#Attach
GameData_Div_stats <- merge(GameData_Divisions, TeamGame_stats, by.x = c("HomeTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(Home_GamesinLast7Days = GamesinLast7Days
         ,Home_Blocked_Percent_prior = Blocked_Percent_prior
         ,Home_Hits_Diff_Avg_prior = Hits_Diff_Avg_prior
         ,Home_streakvalue_prior = streakvalue_prior)



GameData_Div_stats <- merge(GameData_Div_stats, TeamGame_stats, by.x = c("AwayTeam", "GameKey"), by.y = c("FocusTeam", "GameKey")) %>% 
  rename(Away_GamesinLast7Days = GamesinLast7Days
         ,Away_Blocked_Percent_prior = Blocked_Percent_prior
         ,Away_Hits_Diff_Avg_prior = Hits_Diff_Avg_prior
         ,Away_streakvalue_prior = streakvalue_prior)


GameData_Div_stats <- GameData_Div_stats %>% mutate(GamesinLast7Days_Diff = Home_GamesinLast7Days - Away_GamesinLast7Days
                                                    ,Avg_Hits_Diff = Home_Hits_Diff_Avg_prior - Away_Hits_Diff_Avg_prior
                                                    ,StreakValue_Diff = Home_streakvalue_prior - Away_streakvalue_prior)


```



OT vs Opponent, Avg Game Number
```{r}
#i <- 1

GameData_Div_stats <- GameData_Div_stats %>% mutate(Matchup_OTs_prior = NA)

for (i in 1:nrow(GameData_Div_stats)) {

  Matchup_OTs_prior <- GameData_Div_stats %>% filter((HomeTeam == GameData_Div_stats$HomeTeam[i] | HomeTeam == GameData_Div_stats$AwayTeam[i]) &  
                                  (AwayTeam == GameData_Div_stats$HomeTeam[i] | AwayTeam == GameData_Div_stats$AwayTeam[i]) &
                                  Date < Date[i] &
                                  Season == Season[i]
                                ) %>% 
    summarise(Matchup_OTs_prior = sum(OT)) %>% pull()

  
  GameData_Div_stats$Matchup_OTs_prior[i] <- Matchup_OTs_prior
}


GameData_Div_stats <- GameData_Div_stats %>% mutate(Avg_GameNumber = (HomeGameNumber + AwayGameNumber) / 2)
```





```{r}
PredictionData_3 <- GameData_Div_stats %>% filter(HomeGameNumber > 20 & AwayGameNumber > 20) %>% 
  select(GameKey, Season, HomeTeam, AwayTeam, HomeGameNumber, AwayGameNumber, Date, OT, PPG_Diff, Expected_Goals_Diff, USAT_weighted_Diff, FOP_weighted_Diff, SpecialTeamsValue, OTperGame, ContractDifference
         ,DivisionMatchup, ConferenceMatchup, Home_PointsFromPlayoffs, Away_PointsFromPlayoffs, Home_GamesinLast7Days, Away_GamesinLast7Days, GamesinLast7Days_Diff, Home_Blocked_Percent_prior, Away_Blocked_Percent_prior, Home_Hits_Diff_Avg_prior, Away_Hits_Diff_Avg_prior, Avg_Hits_Diff, StreakValue_Diff, Matchup_OTs_prior, Avg_GameNumber) 
```






From Create Winner Predictions


```{r}
load("FO_Data.RData")
load("Goals_Data.RData")
load("Shots_Data.RData")
load("Misc_Data.RData")
load("PP_Data.RData")
```

```{r}
#rename file to go with old code
Goal_Data <- Goals_Data
SAT_Data <- Shots_Data
```

```{r}

FO_Data <- FO_Data %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
FO_Data <-  FO_Data %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
FO_Data <- left_join(FO_Data, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

FO_Data <- FO_Data %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

FO_Data <- FO_Data %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))



SATsAwayTeam <- SAT_Data[grepl("@", SAT_Data$game),]
SATHomeTeam <- SAT_Data[!grepl("@", SAT_Data$game),]

SATHomeTeam <- SATHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
SATHomeTeam <-  SATHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
SATHomeTeam <- left_join(SATHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

SATHomeTeam <- SATHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

SATHomeTeam <- SATHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))


SATsAwayTeam <- SATsAwayTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
SATsAwayTeam <-  SATsAwayTeam %>% mutate( HomeInitl = str_sub(game, start = -3)) #extract home team intl
SATsAwayTeam <- left_join(SATsAwayTeam, TeamInitlKey, by = c("HomeInitl" = "Initl")) #get home team name

SATsAwayTeam <- SATsAwayTeam %>% rename("HomeTeam" = "Name", "AwayTeam" = "team")

SATsAwayTeam <- SATsAwayTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))

#just need the shots from away. the origional has against stats for everything else
SATsAwayTeam <- SATsAwayTeam %>% select(GameKey, shots) %>% rename(away_shots = shots)

SAT_Data <- merge(SATHomeTeam, SATsAwayTeam)


GoalsAwayTeam <- Goal_Data[grepl("@", Goal_Data$game),]
GoalsHomeTeam <- Goal_Data[!grepl("@", Goal_Data$game),]


GoalsHomeTeam <- GoalsHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
GoalsHomeTeam <-  GoalsHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
GoalsHomeTeam <- left_join(GoalsHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

GoalsHomeTeam <- GoalsHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

GoalsHomeTeam <- GoalsHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))



GoalsAwayTeam <- GoalsAwayTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
GoalsAwayTeam <-  GoalsAwayTeam %>% mutate( HomeInitl = str_sub(game, start = -3)) #extract home team intl
GoalsAwayTeam <- left_join(GoalsAwayTeam, TeamInitlKey, by = c("HomeInitl" = "Initl")) #get home team name

GoalsAwayTeam <- GoalsAwayTeam %>% rename("HomeTeam" = "Name", "AwayTeam" = "team")

GoalsAwayTeam <- GoalsAwayTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))

colnames(GoalsHomeTeam) <- c(paste("Home ", colnames(GoalsHomeTeam)))
names(GoalsHomeTeam)[names(GoalsHomeTeam) == 'Home  GameKey'] <- 'GameKey'

colnames(GoalsAwayTeam) <- c(paste("Away ", colnames(GoalsAwayTeam)))
names(GoalsAwayTeam)[names(GoalsAwayTeam) == 'Away  GameKey'] <- 'GameKey'


MiscAwayTeam <- Misc_Data[grepl("@", Misc_Data$game),]
MiscHomeTeam <- Misc_Data[!grepl("@", Misc_Data$game),]


MiscHomeTeam <- MiscHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
MiscHomeTeam <-  MiscHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
MiscHomeTeam <- left_join(MiscHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

MiscHomeTeam <- MiscHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

MiscHomeTeam <- MiscHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))


colnames(MiscHomeTeam) <- c(paste("Home ", colnames(MiscHomeTeam)))
names(MiscHomeTeam)[names(MiscHomeTeam) == 'Home  GameKey'] <- 'GameKey'



MiscAwayTeam <- MiscAwayTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
MiscAwayTeam <-  MiscAwayTeam %>% mutate( HomeInitl = str_sub(game, start = -3)) #extract home team intl
MiscAwayTeam <- left_join(MiscAwayTeam, TeamInitlKey, by = c("HomeInitl" = "Initl")) #get home team name

MiscAwayTeam <- MiscAwayTeam %>% rename("HomeTeam" = "Name", "AwayTeam" = "team")

MiscAwayTeam <- MiscAwayTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))

colnames(MiscAwayTeam) <- c(paste("Away ", colnames(MiscAwayTeam)))
names(MiscAwayTeam)[names(MiscAwayTeam) == 'Away  GameKey'] <- 'GameKey'


PPAwayTeam <- PP_Data[grepl("@", PP_Data$game),]
PPHomeTeam <- PP_Data[!grepl("@", PP_Data$game),]


PPHomeTeam <- PPHomeTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
PPHomeTeam <-  PPHomeTeam %>% mutate( AwayInitl = str_sub(game, start = -3)) #extract away team intl
PPHomeTeam <- left_join(PPHomeTeam, TeamInitlKey, by = c("AwayInitl" = "Initl")) #get away team name

PPHomeTeam <- PPHomeTeam %>% rename("AwayTeam" = "Name", "HomeTeam" = "team")

PPHomeTeam <- PPHomeTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))


colnames(PPHomeTeam) <- c(paste("Home ", colnames(PPHomeTeam)))
names(PPHomeTeam)[names(PPHomeTeam) == 'Home  GameKey'] <- 'GameKey'



PPAwayTeam <- PPAwayTeam %>% mutate( Date =  ymd(substr(game, 1, 10))) #extract date
PPAwayTeam <-  PPAwayTeam %>% mutate( HomeInitl = str_sub(game, start = -3)) #extract home team intl
PPAwayTeam <- left_join(PPAwayTeam, TeamInitlKey, by = c("HomeInitl" = "Initl")) #get home team name

PPAwayTeam <- PPAwayTeam %>% rename("HomeTeam" = "Name", "AwayTeam" = "team")

PPAwayTeam <- PPAwayTeam %>% mutate(GameKey = paste(AwayTeam, " @ ", HomeTeam, " ", Date))

colnames(PPAwayTeam) <- c(paste("Away ", colnames(PPAwayTeam)))
names(PPAwayTeam)[names(PPAwayTeam) == 'Away  GameKey'] <- 'GameKey'


GameDataJoined <- merge(FO_Data, SAT_Data, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, GoalsAwayTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, GoalsHomeTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, MiscAwayTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, MiscHomeTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, PPAwayTeam, by.x = "GameKey", by.y = "GameKey")
GameDataJoined <- merge(GameDataJoined, PPHomeTeam, by.x = "GameKey", by.y = "GameKey")



#remove duplicate columns and unneeded and rename
GameDataJoined_Cleaned <- GameDataJoined %>% select(-index.x, -index.y, -gp.x, -gp.y, -game.x, -HomeTeam.y, -game.y, -Date.y, -AwayInitl.y, -AwayTeam.y, -`Away  index.x`, -`Away  AwayTeam.x`, -`Away  game.x`, -`Away  gp.x`, -`Away  Date.x`, -`Away  HomeInitl.x`, -`Away  HomeTeam.x`, -`Home  index.x`, -`Home  HomeTeam.x`, -`Home  game.x`, -`Home  gp.x`, -`Home  Date.x`, -`Home  AwayInitl.x`, -`Home  AwayTeam.x`, -`Away  index.y`, -`Away  AwayTeam.y`, -`Away  game.y`, -`Away  gp.y`, -`Away  Date.y`, -`Away  HomeInitl.y`, -`Away  HomeTeam.y`, -`Home  index.y`, -`Home  HomeTeam.y`, -`Home  game.y`, -`Home  gp.y`, -`Home  Date.y`, -`Home  AwayInitl.y`, -`Home  AwayTeam.y`, -`Away  AwayTeam`, -`Away  game`, -`Away  gp`, -`Away  Date`, -`Away  HomeInitl`, -`Away  HomeTeam`, -`Home  index`, -`Home  HomeTeam`, -`Home  game`, -`Home  gp`, -`Home  Date`, -`Home  AwayInitl`, -`Home  AwayTeam`, -`Away  index`) %>% rename(HomeTeam = HomeTeam.x, Date = Date.x, AwayInitl = AwayInitl.x, AwayTeam = AwayTeam.x)


```


```{r}
#make season designation
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% mutate(Season = case_when( month(Date) >= 6 ~ paste(year(Date), "-", year(Date) + 1)
                                                                                ,month(Date) < 6 ~ paste(year(Date) - 1, "-", year(Date))
))

GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% arrange(Date)



#convert number format
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>%
    mutate_at(vars(c(3:24, 28:81, 83:93, 95:115, 117:132, 134:139)),list(~as.numeric(str_replace_all(.,'--','0'))))

#convert TOI to seconds from mm:ss
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% mutate(`Away  5v5 TOI/GP` = period_to_seconds(ms(`Away  5v5 TOI/GP`))
                                  ,`Home  5v5 TOI/GP` = period_to_seconds(ms(`Home  5v5 TOI/GP`))
                                  ,`Away  PP TOI/GP`  = period_to_seconds(ms(`Away  PP TOI/GP`))
                                  ,`Home  PP TOI/GP` = period_to_seconds(ms(`Home  PP TOI/GP`))) %>% 
  rename("Away 5v5 TOI" = `Away  5v5 TOI/GP`, "Home 5v5 TOI" = `Home  5v5 TOI/GP`,  "Away PP TOI"= `Away  PP TOI/GP`, "Home PP TOI" = `Home  PP TOI/GP`)

```

```{r}
#make season designation
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% mutate(Season = case_when( month(Date) >= 6 ~ paste(year(Date), "-", year(Date) + 1)
                                                                                ,month(Date) < 6 ~ paste(year(Date) - 1, "-", year(Date))
))

GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% arrange(Date)



#convert number format
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>%
    mutate_at(vars(c(3:24, 28:81, 83:93, 95:115, 117:132, 134:139)),list(~as.numeric(str_replace_all(.,'--','0'))))

#convert TOI to seconds from mm:ss
GameDataJoined_Cleaned <- GameDataJoined_Cleaned %>% mutate(`Away  5v5 TOI/GP` = period_to_seconds(ms(`Away  5v5 TOI/GP`))
                                  ,`Home  5v5 TOI/GP` = period_to_seconds(ms(`Home  5v5 TOI/GP`))
                                  ,`Away  PP TOI/GP`  = period_to_seconds(ms(`Away  PP TOI/GP`))
                                  ,`Home  PP TOI/GP` = period_to_seconds(ms(`Home  PP TOI/GP`))) %>% 
  rename("Away 5v5 TOI" = `Away  5v5 TOI/GP`, "Home 5v5 TOI" = `Home  5v5 TOI/GP`,  "Away PP TOI"= `Away  PP TOI/GP`, "Home PP TOI" = `Home  PP TOI/GP`)

```

```{r}
#make a loop to go through each team and season and extract game data for that team

TeamGameStats <- data.frame()

for (team in TeamInitlKey$Name) {
  
  for (season in unique(GameDataJoined_Cleaned$Season)) {
    
   teamseason <- GameDataJoined_Cleaned %>% filter(Season == season) %>% filter(HomeTeam == team | AwayTeam == team)
   
   teamseason <- teamseason %>% mutate(GameNumber = row_number(), FocusTeam = team) %>% relocate(FocusTeam, GameNumber)
    
   #Adjust stats to be relative to focus team
   teamseason_adj <- data.frame(matrix(NA, nrow = nrow(teamseason), ncol = 0))
   teamseason_adj <- teamseason_adj %>% mutate(FocusTeam = c(teamseason$FocusTeam)
                                               ,Season = season
                                               , GameNumber = teamseason$GameNumber
                                               , GameKey = teamseason$GameKey
                                               , Date = teamseason$Date
                                               #identify if team is home or away
                                               , AwayOrHome = case_when(teamseason$FocusTeam == teamseason$HomeTeam ~ "Home",
                                                                        teamseason$FocusTeam == teamseason$AwayTeam ~ "Away"))
   
   #identify individual stats
   teamseason_adj <- teamseason_adj %>% mutate( 
                               #Faceoff Stats
                               fo = teamseason$fo
                             , fow = case_when(AwayOrHome == "Home" ~ teamseason$fow,
                                               AwayOrHome == "Away" ~ teamseason$fol)
                             , fol = case_when(AwayOrHome == "Home" ~ teamseason$fol,
                                               AwayOrHome == "Away" ~ teamseason$fow)
                             , "fow%" = round( (fow/fo) * 100 ,1 )
                             , ev_fo = teamseason$ev_fo
                             , ev_fow = case_when(AwayOrHome == "Home" ~ teamseason$ev_fow,
                                               AwayOrHome == "Away" ~ teamseason$ev_fol)
                             , ev_fol = case_when(AwayOrHome == "Home" ~ teamseason$ev_fol,
                                               AwayOrHome == "Away" ~ teamseason$ev_fow)
                             , pp_fo = case_when(AwayOrHome == "Home" ~ teamseason$pp_fo,
                                               AwayOrHome == "Away" ~ teamseason$sh_fo)
                             , pp_fow = case_when(AwayOrHome == "Home" ~ teamseason$pp_fow,
                                               AwayOrHome == "Away" ~ teamseason$sh_fol)
                             , pp_fol = case_when(AwayOrHome == "Home" ~ teamseason$pp_fol,
                                               AwayOrHome == "Away" ~ teamseason$sh_fow)
                             , sh_fo = case_when(AwayOrHome == "Home" ~ teamseason$sh_fo,
                                               AwayOrHome == "Away" ~ teamseason$pp_fo)
                             , sh_fow = case_when(AwayOrHome == "Home" ~ teamseason$sh_fow,
                                               AwayOrHome == "Away" ~ teamseason$pp_fol)
                             , sh_fol = case_when(AwayOrHome == "Home" ~ teamseason$sh_fol,
                                               AwayOrHome == "Away" ~ teamseason$pp_fow)
                             , oz_fo = case_when(AwayOrHome == "Home" ~ teamseason$oz_fo,
                                               AwayOrHome == "Away" ~ teamseason$dz_fo)
                             , oz_fow = case_when(AwayOrHome == "Home" ~ teamseason$oz_fow,
                                               AwayOrHome == "Away" ~ teamseason$dz_fol)
                             , oz_fol = case_when(AwayOrHome == "Home" ~ teamseason$oz_fol,
                                               AwayOrHome == "Away" ~ teamseason$dz_fow)
                             , nz_fo = teamseason$nz_fo
                             , nz_fow = case_when(AwayOrHome == "Home" ~ teamseason$nz_fow,
                                               AwayOrHome == "Away" ~ teamseason$nz_fol)
                             , nz_fol = case_when(AwayOrHome == "Home" ~ teamseason$nz_fol,
                                               AwayOrHome == "Away" ~ teamseason$nz_fow)
                             , dz_fo = case_when(AwayOrHome == "Home" ~ teamseason$dz_fo,
                                               AwayOrHome == "Away" ~ teamseason$oz_fo)
                             , dz_fow = case_when(AwayOrHome == "Home" ~ teamseason$dz_fow,
                                               AwayOrHome == "Away" ~ teamseason$oz_fol)
                             , dz_fol = case_when(AwayOrHome == "Home" ~ teamseason$dz_fol,
                                               AwayOrHome == "Away" ~ teamseason$oz_fow)
                             #Shot Stats
                             ,shots = case_when(AwayOrHome == "Home" ~ teamseason$shots,
                                               AwayOrHome == "Away" ~ teamseason$away_shots)
                             ,shots_against = case_when(AwayOrHome == "Home" ~ teamseason$away_shots,
                                               AwayOrHome == "Away" ~ teamseason$shots)
                             ,sat_for = case_when(AwayOrHome == "Home" ~ teamseason$sat_for,
                                               AwayOrHome == "Away" ~ teamseason$sat_against)
                             ,sat_against = case_when(AwayOrHome == "Home" ~ teamseason$sat_against,
                                               AwayOrHome == "Away" ~ teamseason$sat_for)
                             ,sat = sat_for - sat_against 
                             ,sat_tied = case_when(AwayOrHome == "Home" ~ teamseason$sat_tied,
                                               AwayOrHome == "Away" ~ -teamseason$sat_tied)
                             ,sat_ahead = case_when(AwayOrHome == "Home" ~ teamseason$sat_ahead,
                                               AwayOrHome == "Away" ~ -teamseason$sat_behind)
                             ,sat_behind = case_when(AwayOrHome == "Home" ~ teamseason$sat_behind,
                                               AwayOrHome == "Away" ~ -teamseason$sat_ahead)
                             ,sat_close = case_when(AwayOrHome == "Home" ~ teamseason$sat_close,
                                               AwayOrHome == "Away" ~ -teamseason$sat_close)
                             ,usat_for = case_when(AwayOrHome == "Home" ~ teamseason$usat_for,
                                               AwayOrHome == "Away" ~ teamseason$usat_agst)
                             ,usat_agst = case_when(AwayOrHome == "Home" ~ teamseason$usat_agst,
                                               AwayOrHome == "Away" ~ teamseason$usat_for)
                             ,usat = usat_for - usat_agst
                             ,usat_tied = case_when(AwayOrHome == "Home" ~ teamseason$usat_tied,
                                               AwayOrHome == "Away" ~ -teamseason$usat_tied)
                             ,usat_ahead = case_when(AwayOrHome == "Home" ~ teamseason$usat_ahead,
                                               AwayOrHome == "Away" ~ -teamseason$usat_behind)
                             ,usat_behind = case_when(AwayOrHome == "Home" ~ teamseason$usat_behind,
                                               AwayOrHome == "Away" ~ -teamseason$usat_ahead)
                             ,usat_close = case_when(AwayOrHome == "Home" ~ teamseason$usat_close,
                                               AwayOrHome == "Away" ~ -teamseason$usat_close)
                             #Goal Stats
                             ,gf = case_when(AwayOrHome == "Home" ~ teamseason$`Home  gf`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  gf`)
                             ,ga = case_when(AwayOrHome == "Home" ~ teamseason$`Away  gf`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  gf`)
                             ,ev_gf = case_when(AwayOrHome == "Home" ~ teamseason$`Home  ev_gf`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  ev_gf`)
                             ,ev_ga = case_when(AwayOrHome == "Home" ~ teamseason$`Away  ev_gf`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  ev_gf`)
                             ,pp_gf = case_when(AwayOrHome == "Home" ~ teamseason$`Home  pp_gf`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  pp_gf`)
                             ,pp_ga = case_when(AwayOrHome == "Home" ~ teamseason$`Away  pp_gf`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  pp_gf`)
                             ,sh_gf = case_when(AwayOrHome == "Home" ~ teamseason$`Home  sh_gf`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  sh_gf`)
                             ,sh_ga = case_when(AwayOrHome == "Home" ~ teamseason$`Away  sh_gf`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  sh_gf`)
                             ,gf_in_p1 = case_when(AwayOrHome == "Home" ~ teamseason$`Home  gf_in_p1`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  gf_in_p1`)
                             ,ga_in_p1 = case_when(AwayOrHome == "Home" ~ teamseason$`Away  gf_in_p1`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  gf_in_p1`)
                             ,gf_in_p2 = case_when(AwayOrHome == "Home" ~ teamseason$`Home  gf_in_p2`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  gf_in_p2`)
                             ,ga_in_p2 = case_when(AwayOrHome == "Home" ~ teamseason$`Away  gf_in_p2`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  gf_in_p2`)
                             ,gf_in_p3 = case_when(AwayOrHome == "Home" ~ teamseason$`Home  gf_in_p3`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  gf_in_p3`)
                             ,ga_in_p3 = case_when(AwayOrHome == "Home" ~ teamseason$`Away  gf_in_p3`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  gf_in_p3`)
                             ,gf_in_ot = case_when(AwayOrHome == "Home" ~ teamseason$`Home  gf_in_ot`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  gf_in_ot`)
                             ,ga_in_ot = case_when(AwayOrHome == "Home" ~ teamseason$`Away  gf_in_ot`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  gf_in_ot`)
                             #Misc Stats
                             ,`5v5_TOI` = case_when(AwayOrHome == "Home" ~ teamseason$`Home 5v5 TOI`,
                                               AwayOrHome == "Away" ~ teamseason$`Away 5v5 TOI`)
                             ,hits_for = case_when(AwayOrHome == "Home" ~ teamseason$`Home  Hits`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  Hits`)
                             ,hits_agst = case_when(AwayOrHome == "Home" ~ teamseason$`Away  Hits`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  Hits`)
                             ,blks_for = case_when(AwayOrHome == "Home" ~ teamseason$`Home  Bks`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  Bks`)
                             ,blks_agst = case_when(AwayOrHome == "Home" ~ teamseason$`Away  Bks`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  Bks`)
                             ,GvA = case_when(AwayOrHome == "Home" ~ teamseason$`Home  GvA`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  GvA`)
                             ,GvA_opp = case_when(AwayOrHome == "Home" ~ teamseason$`Away  GvA`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  GvA`)
                             ,TkA = case_when(AwayOrHome == "Home" ~ teamseason$`Home  TkA`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  TkA`)
                             ,TkA_opp = case_when(AwayOrHome == "Home" ~ teamseason$`Away  TkA`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  TkA`)
                             ,ENG = case_when(AwayOrHome == "Home" ~ teamseason$`Home  ENG`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  ENG`)
                             ,ENG_opp = case_when(AwayOrHome == "Home" ~ teamseason$`Away  ENG`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  ENG`)
                             ,MsS = case_when(AwayOrHome == "Home" ~ teamseason$`Home  MsS`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  MsS`)
                             ,MsS_opp = case_when(AwayOrHome == "Home" ~ teamseason$`Away  MsS`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  MsS`)
                             #PP stats
                             ,PP_Opp = case_when(AwayOrHome == "Home" ~ teamseason$`Home  PP Opp`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  PP Opp`)
                             ,PP_Opp_Agnst = case_when(AwayOrHome == "Home" ~ teamseason$`Away  PP Opp`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  PP Opp`)  
                             ,`PP%` = case_when(AwayOrHome == "Home" ~ teamseason$`Home  PP%`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  PP%`)
                             ,`PP%_opp` = case_when(AwayOrHome == "Home" ~ teamseason$`Away  PP%`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  PP%`)
                             #General/Computed stats
                             ,W = case_when(AwayOrHome == "Home" ~ teamseason$`Home  w`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  w`)
                             ,L = case_when(AwayOrHome == "Home" ~ teamseason$`Home  l`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  l`)
                             ,OT = case_when(AwayOrHome == "Home" ~ teamseason$`Home  ot`,
                                               AwayOrHome == "Away" ~ teamseason$`Away  ot`)
                             ,`SO` = if_else(gf == ga, 1,0) 
                             ,OT_win = case_when(AwayOrHome == "Home" ~ teamseason$`Away  ot`,
                                               AwayOrHome == "Away" ~ teamseason$`Home  ot`)
                             ,Total_Goals = gf + ga + SO
                    
                             )
                            
   TeamGameStats <- rbind(TeamGameStats, teamseason_adj)
  
  
   
   }
}


#PredictionData <- OddsWithTeamNames %>% select(HomeName,AwayName) %>% 
#  rename(HomeTeam = HomeName, AwayTeam = AwayName) %>% mutate(
#                                               Date = as.Date(gameDate)
#                                               ,Season = SeasonInput
#                                               ,GameKey = paste(AwayTeam, "@", HomeTeam, Date, sep = " ")) %>% 
#  select(GameKey, Date, HomeTeam, AwayTeam, Season) #%>% 
  #mutate(HomeGameNumber = max(TeamGameStats[,FocusTeam == HomeTeam]$GameNumber) +1 )


PredictionData <- GameDataJoined_Cleaned %>% select(GameKey, Date, HomeTeam, AwayTeam, Season) %>% merge(
  TeamGameStats %>% select(FocusTeam, GameNumber, GameKey, W),
  by.x = c("GameKey", "HomeTeam"), by.y = c("GameKey", "FocusTeam")) %>% 
  rename(HomeGameNumber = GameNumber, HomeTeamWin = W) %>% 
  merge(
  TeamGameStats %>% select(FocusTeam, GameNumber, GameKey, Total_Goals),
  by.x = c("GameKey", "AwayTeam"), by.y = c("GameKey", "FocusTeam")) %>% 
  rename(AwayGameNumber = GameNumber) %>% 
  arrange(Date)

PredictionData <- PredictionData %>% select(GameKey, Date, HomeTeam, AwayTeam, Season, HomeGameNumber, AwayGameNumber, HomeTeamWin, Total_Goals)

#not predicting for first 5 games of season. Use those to get grouped stats
PredictionData <- PredictionData %>% filter(HomeGameNumber > 5 & AwayGameNumber > 5)




TotalPredictionData <- data.frame()

for (i in 1:nrow(PredictionData)) {
 
  HomePastStats <-  data.frame(matrix(NA, nrow = 1, ncol = 0))
  AwayPastStats <-  data.frame(matrix(NA, nrow = 1, ncol = 0))
  HomePastStats_last5 <-  data.frame(matrix(NA, nrow = 1, ncol = 0))
  AwayPastStats_last5 <-  data.frame(matrix(NA, nrow = 1, ncol = 0))
   
  selectedgame <- PredictionData[i,]
  
  HomeGamesToSum <- TeamGameStats %>% filter(FocusTeam == selectedgame$HomeTeam
                                             #, GameNumber < selectedgame$HomeGameNumber
                                             , Season == selectedgame$Season)
  
  AwayGamesToSum <- TeamGameStats %>% filter(FocusTeam == selectedgame$AwayTeam
                                             #, GameNumber < selectedgame$AwayGameNumber
                                             , Season == selectedgame$Season)
 
  #Calculate Home Past Performance 
  HomePastStats <- HomePastStats %>% mutate(
    HomeGameNumber = max(HomeGamesToSum$GameNumber) + 1
    ,AwayGameNumber = max(AwayGamesToSum$GameNumber) + 1
    ,HomeTeamWin = 0 #dummy
    ,Total_Goals = 0 #dummy #these first 4 are dummies for placement correctness
    ,home_fo_avg = sum(HomeGamesToSum$fo)/ nrow(HomeGamesToSum)
    ,home_fow_avg = sum(HomeGamesToSum$fow)/ nrow(HomeGamesToSum)
    ,home_fol_avg = sum(HomeGamesToSum$fol)/ nrow(HomeGamesToSum)
    ,`home_fow%` = sum(HomeGamesToSum$fow)/sum(HomeGamesToSum$fo)
    ,home_ev_fo_avg = sum(HomeGamesToSum$ev_fo)/ nrow(HomeGamesToSum)
    ,home_ev_fow_avg = sum(HomeGamesToSum$ev_fow)/ nrow(HomeGamesToSum)
    ,home_ev_fol_avg = sum(HomeGamesToSum$ev_fol)/ nrow(HomeGamesToSum)
    ,`home_ev_fow%` = sum(HomeGamesToSum$ev_fow)/sum(HomeGamesToSum$ev_fo)
    ,home_pp_fo_avg = sum(HomeGamesToSum$pp_fo)/ nrow(HomeGamesToSum)
    ,home_pp_fow_avg = sum(HomeGamesToSum$pp_fow)/ nrow(HomeGamesToSum)
    ,home_pp_fol_avg = sum(HomeGamesToSum$pp_fol)/ nrow(HomeGamesToSum)
    ,`home_pp_fow%` = sum(HomeGamesToSum$pp_fow)/sum(HomeGamesToSum$pp_fo)
    ,home_sh_fo_avg = sum(HomeGamesToSum$sh_fo)/ nrow(HomeGamesToSum)
    ,home_sh_fow_avg = sum(HomeGamesToSum$sh_fow)/ nrow(HomeGamesToSum)
    ,home_sh_fol_avg = sum(HomeGamesToSum$sh_fol)/ nrow(HomeGamesToSum)
    ,`home_sh_fow%` = sum(HomeGamesToSum$sh_fow)/sum(HomeGamesToSum$sh_fo)
    ,home_oz_fo_avg = sum(HomeGamesToSum$oz_fo)/ nrow(HomeGamesToSum)
    ,home_oz_fow_avg = sum(HomeGamesToSum$oz_fow)/ nrow(HomeGamesToSum)
    ,home_oz_fol_avg = sum(HomeGamesToSum$oz_fol)/ nrow(HomeGamesToSum)
    ,`home_oz_fow%` = sum(HomeGamesToSum$oz_fow)/sum(HomeGamesToSum$oz_fo)
    ,home_nz_fo_avg = sum(HomeGamesToSum$nz_fo)/ nrow(HomeGamesToSum)
    ,home_nz_fow_avg = sum(HomeGamesToSum$nz_fow)/ nrow(HomeGamesToSum)
    ,home_nz_fol_avg = sum(HomeGamesToSum$nz_fol)/ nrow(HomeGamesToSum)
    ,`home_nz_fow%` = sum(HomeGamesToSum$nz_fow)/sum(HomeGamesToSum$nz_fo)
    ,home_dz_fo_avg = sum(HomeGamesToSum$dz_fo)/ nrow(HomeGamesToSum)
    ,home_dz_fow_avg = sum(HomeGamesToSum$dz_fow)/ nrow(HomeGamesToSum)
    ,home_dz_fol_avg = sum(HomeGamesToSum$dz_fol)/ nrow(HomeGamesToSum)
    ,`home_dz_fow%` = sum(HomeGamesToSum$dz_fow)/sum(HomeGamesToSum$dz_fo)
    ,home_shots_avg = sum(HomeGamesToSum$shots)/nrow(HomeGamesToSum)
    ,home_shots_against_avg = sum(HomeGamesToSum$shots_against)/nrow(HomeGamesToSum)
    ,home_sat_for_avg = sum(HomeGamesToSum$sat_for)/nrow(HomeGamesToSum)
    ,home_sat_against_avg = sum(HomeGamesToSum$sat_against)/nrow(HomeGamesToSum)
    ,home_sat_avg = sum(HomeGamesToSum$sat)/nrow(HomeGamesToSum)
    ,home_sat_total = sum(HomeGamesToSum$sat)
    ,home_sat_tied_avg = sum(HomeGamesToSum$sat_tied)/nrow(HomeGamesToSum)
    ,home_sat_tied_total = sum(HomeGamesToSum$sat_tied)
    ,home_sat_ahead_avg = sum(HomeGamesToSum$sat_ahead)/nrow(HomeGamesToSum)
    ,home_sat_ahead_total = sum(HomeGamesToSum$sat_ahead)
    ,home_sat_behind_avg = sum(HomeGamesToSum$sat_behind)/nrow(HomeGamesToSum)
    ,home_sat_behind_total = sum(HomeGamesToSum$sat_behind)
    ,home_sat_close_avg = sum(HomeGamesToSum$sat_close)/nrow(HomeGamesToSum)
    ,home_sat_close_total = sum(HomeGamesToSum$sat_close)
    ,home_usat_for_avg = sum(HomeGamesToSum$usat_for)/nrow(HomeGamesToSum)
    ,home_usat_against_avg = sum(HomeGamesToSum$usat_agst)/nrow(HomeGamesToSum)
    ,home_usat_avg = sum(HomeGamesToSum$usat)/nrow(HomeGamesToSum)
    ,home_usat_total = sum(HomeGamesToSum$usat)
    ,home_usat_tied_avg = sum(HomeGamesToSum$usat_tied)/nrow(HomeGamesToSum)
    ,home_usat_tied_total = sum(HomeGamesToSum$usat_tied)
    ,home_usat_ahead_avg = sum(HomeGamesToSum$usat_ahead)/nrow(HomeGamesToSum)
    ,home_usat_ahead_total = sum(HomeGamesToSum$usat_ahead)
    ,home_usat_behind_avg = sum(HomeGamesToSum$usat_behind)/nrow(HomeGamesToSum)
    ,home_usat_behind_total = sum(HomeGamesToSum$usat_behind)
    ,home_usat_close_avg = sum(HomeGamesToSum$usat_close)/nrow(HomeGamesToSum)
    ,home_usat_close_total = sum(HomeGamesToSum$usat_close)
    ,home_gf_avg = sum(HomeGamesToSum$gf)/nrow(HomeGamesToSum)
    ,home_ga_avg = sum(HomeGamesToSum$ga)/nrow(HomeGamesToSum)
    ,home_goal_diff_avg = sum(HomeGamesToSum$gf - HomeGamesToSum$ga) / nrow(HomeGamesToSum)
    ,home_goal_diff_total = sum(HomeGamesToSum$gf - HomeGamesToSum$ga)
    ,home_ev_gf_avg = sum(HomeGamesToSum$ev_gf)/nrow(HomeGamesToSum)
    ,home_ev_ga_avg = sum(HomeGamesToSum$ev_ga)/nrow(HomeGamesToSum)
    ,home_ev_goal_diff_avg = sum(HomeGamesToSum$ev_gf - HomeGamesToSum$ev_ga) / nrow(HomeGamesToSum)
    ,home_ev_goal_diff_total = sum(HomeGamesToSum$ev_gf - HomeGamesToSum$ev_ga)
    ,home_pp_gf_avg = sum(HomeGamesToSum$pp_gf)/nrow(HomeGamesToSum)
    ,home_pp_ga_avg = sum(HomeGamesToSum$pp_ga)/nrow(HomeGamesToSum)
    ,home_pp_goal_diff_avg = sum(HomeGamesToSum$pp_gf - HomeGamesToSum$pp_ga) / nrow(HomeGamesToSum)
    ,home_pp_goal_diff_total = sum(HomeGamesToSum$pp_gf - HomeGamesToSum$pp_ga)
    ,home_sh_gf_avg = sum(HomeGamesToSum$sh_gf)/nrow(HomeGamesToSum)
    ,home_sh_ga_avg = sum(HomeGamesToSum$sh_ga)/nrow(HomeGamesToSum)
    ,home_sh_goal_diff_avg = sum(HomeGamesToSum$sh_gf - HomeGamesToSum$sh_ga) / nrow(HomeGamesToSum)
    ,home_sh_goal_diff_total = sum(HomeGamesToSum$sh_gf - HomeGamesToSum$sh_ga)
    ,home_gf_in_p1_avg = sum(HomeGamesToSum$gf_in_p1)/nrow(HomeGamesToSum)
    ,home_ga_in_p1_avg = sum(HomeGamesToSum$ga_in_p1)/nrow(HomeGamesToSum)
    ,home_goal_in_p1_diff_avg = sum(HomeGamesToSum$gf_in_p1 - HomeGamesToSum$ga_in_p1) / nrow(HomeGamesToSum)
    ,home_goal_in_p1_diff_total = sum(HomeGamesToSum$gf_in_p1 - HomeGamesToSum$ga_in_p1)
    ,home_gf_in_p2_avg = sum(HomeGamesToSum$gf_in_p2)/nrow(HomeGamesToSum)
    ,home_ga_in_p2_avg = sum(HomeGamesToSum$ga_in_p2)/nrow(HomeGamesToSum)
    ,home_goal_in_p2_diff_avg = sum(HomeGamesToSum$gf_in_p2 - HomeGamesToSum$ga_in_p2) / nrow(HomeGamesToSum)
    ,home_goal_in_p2_diff_total = sum(HomeGamesToSum$gf_in_p2 - HomeGamesToSum$ga_in_p2)
    ,home_gf_in_p3_avg = sum(HomeGamesToSum$gf_in_p3)/nrow(HomeGamesToSum)
    ,home_ga_in_p3_avg = sum(HomeGamesToSum$ga_in_p3)/nrow(HomeGamesToSum)
    ,home_goal_in_p3_diff_avg = sum(HomeGamesToSum$gf_in_p3 - HomeGamesToSum$ga_in_p3) / nrow(HomeGamesToSum)
    ,home_goal_in_p3_diff_total = sum(HomeGamesToSum$gf_in_p3 - HomeGamesToSum$ga_in_p3)
    ,home_gf_in_ot_avg = sum(HomeGamesToSum$gf_in_ot)/nrow(HomeGamesToSum)
    ,home_ga_in_ot_avg = sum(HomeGamesToSum$ga_in_ot)/nrow(HomeGamesToSum)
    ,home_goal_in_ot_diff_avg = sum(HomeGamesToSum$gf_in_ot - HomeGamesToSum$ga_in_ot) / nrow(HomeGamesToSum)
    ,home_goal_in_ot_diff_total = sum(HomeGamesToSum$gf_in_ot - HomeGamesToSum$ga_in_ot)
    ,home_5v5_TOI_avg = sum(HomeGamesToSum$`5v5_TOI`) / nrow(HomeGamesToSum)
    ,home_hits_for_avg = sum(HomeGamesToSum$hits_for)/nrow(HomeGamesToSum)
    ,home_hits_agst_avg = sum(HomeGamesToSum$hits_agst)/nrow(HomeGamesToSum)
    ,home_hits_diff_avg = sum(HomeGamesToSum$hits_for - HomeGamesToSum$hits_agst) / nrow(HomeGamesToSum)
    ,home_hits_diff_total = sum(HomeGamesToSum$hits_for - HomeGamesToSum$hits_agst)
    ,home_blks_for_avg = sum(HomeGamesToSum$blks_for)/nrow(HomeGamesToSum)
    ,home_blks_agst_avg = sum(HomeGamesToSum$blks_agst)/nrow(HomeGamesToSum)
    ,home_blks_diff_avg = sum(HomeGamesToSum$blks_for - HomeGamesToSum$blks_agst) / nrow(HomeGamesToSum)
    ,home_blks_diff_total = sum(HomeGamesToSum$blks_for - HomeGamesToSum$blks_agst)
    ,home_GvA_avg = sum(HomeGamesToSum$GvA)/nrow(HomeGamesToSum)
    ,home_TkA_avg = sum(HomeGamesToSum$TkA)/nrow(HomeGamesToSum)
    ,home_ENG_avg = sum(HomeGamesToSum$ENG)/nrow(HomeGamesToSum)
    ,home_ENG_opp_avg = sum(HomeGamesToSum$ENG_opp)/nrow(HomeGamesToSum)
    ,home_MsS_avg = sum(HomeGamesToSum$MsS)/nrow(HomeGamesToSum)
    ,home_PP_Opp_avg = sum(HomeGamesToSum$PP_Opp)/nrow(HomeGamesToSum)
    ,`home_PP%` = sum(HomeGamesToSum$pp_gf) / sum(HomeGamesToSum$PP_Opp)
    ,home_PP_Opp_agnst_avg = sum(HomeGamesToSum$PP_Opp_Agnst)/nrow(HomeGamesToSum)
    ,`home_PenatlyKill%` = 1- (sum(HomeGamesToSum$pp_ga) / sum(HomeGamesToSum$PP_Opp_Agnst))
    ,home_W = sum(HomeGamesToSum$W)
    ,home_L = sum(HomeGamesToSum$L)
    ,home_OT = sum(HomeGamesToSum$OT)
    ,home_Pts = (2 * home_W) + home_OT
    ,`home_Pt%` = home_Pts / (2*nrow(HomeGamesToSum))
    ,home_SO = sum(HomeGamesToSum$SO)
    ,home_OT_win = sum(HomeGamesToSum$OT_win)
    ,home_days_since_last_game = as.integer(selectedgame$Date - max(HomeGamesToSum$Date))
    
     )
  
  #winning streak -- found here: https://www.r-bloggers.com/2020/06/detecting-streaks-in-r/
  HomeStreakTable <- HomeGamesToSum %>% select(W,L,OT) %>% mutate(lagged=lag(W)) %>% #note: that's dplyr::lag, not stats::lag
mutate(start=(W != lagged))
HomeStreakTable[1, "start"] <- TRUE
HomeStreakTable <- HomeStreakTable %>% mutate(streak_id=cumsum(start))
HomeStreakTable <- HomeStreakTable %>% group_by(streak_id) %>% mutate(streak=row_number()) %>%
ungroup()
#new part to make it negative for losing streak
HomeStreakTable <- HomeStreakTable %>% mutate(streakvalue = case_when(W == 0 ~ -streak,
                                                   W == 1 ~ streak))
HomePastStats <- HomePastStats %>% mutate(home_Winning_Streak = HomeStreakTable$streakvalue[nrow(HomeStreakTable)])
  
  
  
  #Calculate Away Past Performance 
  AwayPastStats <- AwayPastStats %>% mutate(
    away_fo_avg = sum(AwayGamesToSum$fo)/ nrow(AwayGamesToSum)
    ,away_fow_avg = sum(AwayGamesToSum$fow)/ nrow(AwayGamesToSum)
    ,away_fol_avg = sum(AwayGamesToSum$fol)/ nrow(AwayGamesToSum)
    ,`away_fow%` = sum(AwayGamesToSum$fow)/sum(AwayGamesToSum$fo)
    ,away_ev_fo_avg = sum(AwayGamesToSum$ev_fo)/ nrow(AwayGamesToSum)
    ,away_ev_fow_avg = sum(AwayGamesToSum$ev_fow)/ nrow(AwayGamesToSum)
    ,away_ev_fol_avg = sum(AwayGamesToSum$ev_fol)/ nrow(AwayGamesToSum)
    ,`away_ev_fow%` = sum(AwayGamesToSum$ev_fow)/sum(AwayGamesToSum$ev_fo)
    ,away_pp_fo_avg = sum(AwayGamesToSum$pp_fo)/ nrow(AwayGamesToSum)
    ,away_pp_fow_avg = sum(AwayGamesToSum$pp_fow)/ nrow(AwayGamesToSum)
    ,away_pp_fol_avg = sum(AwayGamesToSum$pp_fol)/ nrow(AwayGamesToSum)
    ,`away_pp_fow%` = sum(AwayGamesToSum$pp_fow)/sum(AwayGamesToSum$pp_fo)
    ,away_sh_fo_avg = sum(AwayGamesToSum$sh_fo)/ nrow(AwayGamesToSum)
    ,away_sh_fow_avg = sum(AwayGamesToSum$sh_fow)/ nrow(AwayGamesToSum)
    ,away_sh_fol_avg = sum(AwayGamesToSum$sh_fol)/ nrow(AwayGamesToSum)
    ,`away_sh_fow%` = sum(AwayGamesToSum$sh_fow)/sum(AwayGamesToSum$sh_fo)
    ,away_oz_fo_avg = sum(AwayGamesToSum$oz_fo)/ nrow(AwayGamesToSum)
    ,away_oz_fow_avg = sum(AwayGamesToSum$oz_fow)/ nrow(AwayGamesToSum)
    ,away_oz_fol_avg = sum(AwayGamesToSum$oz_fol)/ nrow(AwayGamesToSum)
    ,`away_oz_fow%` = sum(AwayGamesToSum$oz_fow)/sum(AwayGamesToSum$oz_fo)
    ,away_nz_fo_avg = sum(AwayGamesToSum$nz_fo)/ nrow(AwayGamesToSum)
    ,away_nz_fow_avg = sum(AwayGamesToSum$nz_fow)/ nrow(AwayGamesToSum)
    ,away_nz_fol_avg = sum(AwayGamesToSum$nz_fol)/ nrow(AwayGamesToSum)
    ,`away_nz_fow%` = sum(AwayGamesToSum$nz_fow)/sum(AwayGamesToSum$nz_fo)
    ,away_dz_fo_avg = sum(AwayGamesToSum$dz_fo)/ nrow(AwayGamesToSum)
    ,away_dz_fow_avg = sum(AwayGamesToSum$dz_fow)/ nrow(AwayGamesToSum)
    ,away_dz_fol_avg = sum(AwayGamesToSum$dz_fol)/ nrow(AwayGamesToSum)
    ,`away_dz_fow%` = sum(AwayGamesToSum$dz_fow)/sum(AwayGamesToSum$dz_fo)
    ,away_shots_avg = sum(AwayGamesToSum$shots)/nrow(AwayGamesToSum)
    ,away_shots_against_avg = sum(AwayGamesToSum$shots_against)/nrow(AwayGamesToSum)
    ,away_sat_for_avg = sum(AwayGamesToSum$sat_for)/nrow(AwayGamesToSum)
    ,away_sat_against_avg = sum(AwayGamesToSum$sat_against)/nrow(AwayGamesToSum)
    ,away_sat_avg = sum(AwayGamesToSum$sat)/nrow(AwayGamesToSum)
    ,away_sat_total = sum(AwayGamesToSum$sat)
    ,away_sat_tied_avg = sum(AwayGamesToSum$sat_tied)/nrow(AwayGamesToSum)
    ,away_sat_tied_total = sum(AwayGamesToSum$sat_tied)
    ,away_sat_ahead_avg = sum(AwayGamesToSum$sat_ahead)/nrow(AwayGamesToSum)
    ,away_sat_ahead_total = sum(AwayGamesToSum$sat_ahead)
    ,away_sat_behind_avg = sum(AwayGamesToSum$sat_behind)/nrow(AwayGamesToSum)
    ,away_sat_behind_total = sum(AwayGamesToSum$sat_behind)
    ,away_sat_close_avg = sum(AwayGamesToSum$sat_close)/nrow(AwayGamesToSum)
    ,away_sat_close_total = sum(AwayGamesToSum$sat_close)
    ,away_usat_for_avg = sum(AwayGamesToSum$usat_for)/nrow(AwayGamesToSum)
    ,away_usat_against_avg = sum(AwayGamesToSum$usat_agst)/nrow(AwayGamesToSum)
    ,away_usat_avg = sum(AwayGamesToSum$usat)/nrow(AwayGamesToSum)
    ,away_usat_total = sum(AwayGamesToSum$usat)
    ,away_usat_tied_avg = sum(AwayGamesToSum$usat_tied)/nrow(AwayGamesToSum)
    ,away_usat_tied_total = sum(AwayGamesToSum$usat_tied)
    ,away_usat_ahead_avg = sum(AwayGamesToSum$usat_ahead)/nrow(AwayGamesToSum)
    ,away_usat_ahead_total = sum(AwayGamesToSum$usat_ahead)
    ,away_usat_behind_avg = sum(AwayGamesToSum$usat_behind)/nrow(AwayGamesToSum)
    ,away_usat_behind_total = sum(AwayGamesToSum$usat_behind)
    ,away_usat_close_avg = sum(AwayGamesToSum$usat_close)/nrow(AwayGamesToSum)
    ,away_usat_close_total = sum(AwayGamesToSum$usat_close)
    ,away_gf_avg = sum(AwayGamesToSum$gf)/nrow(AwayGamesToSum)
    ,away_ga_avg = sum(AwayGamesToSum$ga)/nrow(AwayGamesToSum)
    ,away_goal_diff_avg = sum(AwayGamesToSum$gf - AwayGamesToSum$ga) / nrow(AwayGamesToSum)
    ,away_goal_diff_total = sum(AwayGamesToSum$gf - AwayGamesToSum$ga)
    ,away_ev_gf_avg = sum(AwayGamesToSum$ev_gf)/nrow(AwayGamesToSum)
    ,away_ev_ga_avg = sum(AwayGamesToSum$ev_ga)/nrow(AwayGamesToSum)
    ,away_ev_goal_diff_avg = sum(AwayGamesToSum$ev_gf - AwayGamesToSum$ev_ga) / nrow(AwayGamesToSum)
    ,away_ev_goal_diff_total = sum(AwayGamesToSum$ev_gf - AwayGamesToSum$ev_ga)
    ,away_pp_gf_avg = sum(AwayGamesToSum$pp_gf)/nrow(AwayGamesToSum)
    ,away_pp_ga_avg = sum(AwayGamesToSum$pp_ga)/nrow(AwayGamesToSum)
    ,away_pp_goal_diff_avg = sum(AwayGamesToSum$pp_gf - AwayGamesToSum$pp_ga) / nrow(AwayGamesToSum)
    ,away_pp_goal_diff_total = sum(AwayGamesToSum$pp_gf - AwayGamesToSum$pp_ga)
    ,away_sh_gf_avg = sum(AwayGamesToSum$sh_gf)/nrow(AwayGamesToSum)
    ,away_sh_ga_avg = sum(AwayGamesToSum$sh_ga)/nrow(AwayGamesToSum)
    ,away_sh_goal_diff_avg = sum(AwayGamesToSum$sh_gf - AwayGamesToSum$sh_ga) / nrow(AwayGamesToSum)
    ,away_sh_goal_diff_total = sum(AwayGamesToSum$sh_gf - AwayGamesToSum$sh_ga)
    ,away_gf_in_p1_avg = sum(AwayGamesToSum$gf_in_p1)/nrow(AwayGamesToSum)
    ,away_ga_in_p1_avg = sum(AwayGamesToSum$ga_in_p1)/nrow(AwayGamesToSum)
    ,away_goal_in_p1_diff_avg = sum(AwayGamesToSum$gf_in_p1 - AwayGamesToSum$ga_in_p1) / nrow(AwayGamesToSum)
    ,away_goal_in_p1_diff_total = sum(AwayGamesToSum$gf_in_p1 - AwayGamesToSum$ga_in_p1)
    ,away_gf_in_p2_avg = sum(AwayGamesToSum$gf_in_p2)/nrow(AwayGamesToSum)
    ,away_ga_in_p2_avg = sum(AwayGamesToSum$ga_in_p2)/nrow(AwayGamesToSum)
    ,away_goal_in_p2_diff_avg = sum(AwayGamesToSum$gf_in_p2 - AwayGamesToSum$ga_in_p2) / nrow(AwayGamesToSum)
    ,away_goal_in_p2_diff_total = sum(AwayGamesToSum$gf_in_p2 - AwayGamesToSum$ga_in_p2)
    ,away_gf_in_p3_avg = sum(AwayGamesToSum$gf_in_p3)/nrow(AwayGamesToSum)
    ,away_ga_in_p3_avg = sum(AwayGamesToSum$ga_in_p3)/nrow(AwayGamesToSum)
    ,away_goal_in_p3_diff_avg = sum(AwayGamesToSum$gf_in_p3 - AwayGamesToSum$ga_in_p3) / nrow(AwayGamesToSum)
    ,away_goal_in_p3_diff_total = sum(AwayGamesToSum$gf_in_p3 - AwayGamesToSum$ga_in_p3)
    ,away_gf_in_ot_avg = sum(AwayGamesToSum$gf_in_ot)/nrow(AwayGamesToSum)
    ,away_ga_in_ot_avg = sum(AwayGamesToSum$ga_in_ot)/nrow(AwayGamesToSum)
    ,away_goal_in_ot_diff_avg = sum(AwayGamesToSum$gf_in_ot - AwayGamesToSum$ga_in_ot) / nrow(AwayGamesToSum)
    ,away_goal_in_ot_diff_total = sum(AwayGamesToSum$gf_in_ot - AwayGamesToSum$ga_in_ot)
    ,away_5v5_TOI_avg = sum(AwayGamesToSum$`5v5_TOI`) / nrow(AwayGamesToSum)
    ,away_hits_for_avg = sum(AwayGamesToSum$hits_for)/nrow(AwayGamesToSum)
    ,away_hits_agst_avg = sum(AwayGamesToSum$hits_agst)/nrow(AwayGamesToSum)
    ,away_hits_diff_avg = sum(AwayGamesToSum$hits_for - AwayGamesToSum$hits_agst) / nrow(AwayGamesToSum)
    ,away_hits_diff_total = sum(AwayGamesToSum$hits_for - AwayGamesToSum$hits_agst)
    ,away_blks_for_avg = sum(AwayGamesToSum$blks_for)/nrow(AwayGamesToSum)
    ,away_blks_agst_avg = sum(AwayGamesToSum$blks_agst)/nrow(AwayGamesToSum)
    ,away_blks_diff_avg = sum(AwayGamesToSum$blks_for - AwayGamesToSum$blks_agst) / nrow(AwayGamesToSum)
    ,away_blks_diff_total = sum(AwayGamesToSum$blks_for - AwayGamesToSum$blks_agst)
    ,away_GvA_avg = sum(AwayGamesToSum$GvA)/nrow(AwayGamesToSum)
    ,away_TkA_avg = sum(AwayGamesToSum$TkA)/nrow(AwayGamesToSum)
    ,away_ENG_avg = sum(AwayGamesToSum$ENG)/nrow(AwayGamesToSum)
    ,away_ENG_opp_avg = sum(AwayGamesToSum$ENG_opp)/nrow(AwayGamesToSum)
    ,away_MsS_avg = sum(AwayGamesToSum$MsS)/nrow(AwayGamesToSum)
    ,away_PP_Opp_avg = sum(AwayGamesToSum$PP_Opp)/nrow(AwayGamesToSum)
    ,`away_PP%` = sum(AwayGamesToSum$pp_gf) / sum(AwayGamesToSum$PP_Opp)
    ,away_PP_Opp_agnst_avg = sum(AwayGamesToSum$PP_Opp_Agnst)/nrow(AwayGamesToSum)
    ,`away_PenatlyKill%` = 1- (sum(AwayGamesToSum$pp_ga) / sum(AwayGamesToSum$PP_Opp_Agnst))
    ,away_W = sum(AwayGamesToSum$W)
    ,away_L = sum(AwayGamesToSum$L)
    ,away_OT = sum(AwayGamesToSum$OT)
    ,away_Pts = (2 * away_W) + away_OT
    ,`away_Pt%` = away_Pts / (2*nrow(AwayGamesToSum))
    ,away_SO = sum(AwayGamesToSum$SO)
    ,away_OT_win = sum(AwayGamesToSum$OT_win)
    ,away_days_since_last_game = as.integer(selectedgame$Date - max(AwayGamesToSum$Date))
    
     )
  
  
  #winning streak -- found here: https://www.r-bloggers.com/2020/06/detecting-streaks-in-r/
  AwayStreakTable <- AwayGamesToSum %>% select(W,L,OT) %>% mutate(lagged=lag(W)) %>% #note: that's dplyr::lag, not stats::lag
mutate(start=(W != lagged))
AwayStreakTable[1, "start"] <- TRUE
AwayStreakTable <- AwayStreakTable %>% mutate(streak_id=cumsum(start))
AwayStreakTable <- AwayStreakTable %>% group_by(streak_id) %>% mutate(streak=row_number()) %>%
ungroup()
#new part to make it negative for losing streak
AwayStreakTable <- AwayStreakTable %>% mutate(streakvalue = case_when(W == 0 ~ -streak,
                                                   W == 1 ~ streak))
AwayPastStats <- AwayPastStats %>% mutate(away_Winning_Streak = AwayStreakTable$streakvalue[nrow(AwayStreakTable)])
  
  
  #stats for just last 5 games for recent trends
  HomeGamesToSum_last5 <- TeamGameStats %>% filter(FocusTeam == selectedgame$HomeTeam
                                                   #, GameNumber < selectedgame$HomeGameNumber
                                                     #selectedgame$HomeGameNumber
                                                   , GameNumber >= max(HomeGamesToSum$GameNumber) - 4
                                                     #selectedgame$HomeGameNumber - 5
                                                   ,Season == selectedgame$Season)

  HomePastStats_last5 <- HomePastStats_last5 %>% mutate(
    home_fo_avg_last5 = sum(HomeGamesToSum_last5$fo)/ nrow(HomeGamesToSum_last5)
    ,home_fow_avg_last5 = sum(HomeGamesToSum_last5$fow)/ nrow(HomeGamesToSum_last5)
    ,home_fol_avg_last5 = sum(HomeGamesToSum_last5$fol)/ nrow(HomeGamesToSum_last5)
    ,`home_fow%_last5` = sum(HomeGamesToSum_last5$fow)/sum(HomeGamesToSum_last5$fo)
    ,home_ev_fo_avg_last5 = sum(HomeGamesToSum_last5$ev_fo)/ nrow(HomeGamesToSum_last5)
    ,home_ev_fow_avg_last5 = sum(HomeGamesToSum_last5$ev_fow)/ nrow(HomeGamesToSum_last5)
    ,home_ev_fol_avg_last5 = sum(HomeGamesToSum_last5$ev_fol)/ nrow(HomeGamesToSum_last5)
    ,`home_ev_fow%_last5` = sum(HomeGamesToSum_last5$ev_fow)/sum(HomeGamesToSum_last5$ev_fo)
    ,home_pp_fo_avg_last5 = sum(HomeGamesToSum_last5$pp_fo)/ nrow(HomeGamesToSum_last5)
    ,home_pp_fow_avg_last5 = sum(HomeGamesToSum_last5$pp_fow)/ nrow(HomeGamesToSum_last5)
    ,home_pp_fol_avg_last5 = sum(HomeGamesToSum_last5$pp_fol)/ nrow(HomeGamesToSum_last5)
    ,`home_pp_fow%_last5` = sum(HomeGamesToSum_last5$pp_fow)/sum(HomeGamesToSum_last5$pp_fo)
    ,home_sh_fo_avg_last5 = sum(HomeGamesToSum_last5$sh_fo)/ nrow(HomeGamesToSum_last5)
    ,home_sh_fow_avg_last5 = sum(HomeGamesToSum_last5$sh_fow)/ nrow(HomeGamesToSum_last5)
    ,home_sh_fol_avg_last5 = sum(HomeGamesToSum_last5$sh_fol)/ nrow(HomeGamesToSum_last5)
    ,`home_sh_fow%_last5` = sum(HomeGamesToSum_last5$sh_fow)/sum(HomeGamesToSum_last5$sh_fo)
    ,home_oz_fo_avg_last5 = sum(HomeGamesToSum_last5$oz_fo)/ nrow(HomeGamesToSum_last5)
    ,home_oz_fow_avg_last5 = sum(HomeGamesToSum_last5$oz_fow)/ nrow(HomeGamesToSum_last5)
    ,home_oz_fol_avg_last5 = sum(HomeGamesToSum_last5$oz_fol)/ nrow(HomeGamesToSum_last5)
    ,`home_oz_fow%_last5` = sum(HomeGamesToSum_last5$oz_fow)/sum(HomeGamesToSum_last5$oz_fo)
    ,home_nz_fo_avg_last5 = sum(HomeGamesToSum_last5$nz_fo)/ nrow(HomeGamesToSum_last5)
    ,home_nz_fow_avg_last5 = sum(HomeGamesToSum_last5$nz_fow)/ nrow(HomeGamesToSum_last5)
    ,home_nz_fol_avg_last5 = sum(HomeGamesToSum_last5$nz_fol)/ nrow(HomeGamesToSum_last5)
    ,`home_nz_fow%_last5` = sum(HomeGamesToSum_last5$nz_fow)/sum(HomeGamesToSum_last5$nz_fo)
    ,home_dz_fo_avg_last5 = sum(HomeGamesToSum_last5$dz_fo)/ nrow(HomeGamesToSum_last5)
    ,home_dz_fow_avg_last5 = sum(HomeGamesToSum_last5$dz_fow)/ nrow(HomeGamesToSum_last5)
    ,home_dz_fol_avg_last5 = sum(HomeGamesToSum_last5$dz_fol)/ nrow(HomeGamesToSum_last5)
    ,`home_dz_fow%_last5` = sum(HomeGamesToSum_last5$dz_fow)/sum(HomeGamesToSum_last5$dz_fo)
    ,home_shots_avg_last5 = sum(HomeGamesToSum_last5$shots)/nrow(HomeGamesToSum_last5)
    ,home_shots_against_avg_last5 = sum(HomeGamesToSum_last5$shots_against)/nrow(HomeGamesToSum_last5)
    ,home_sat_for_avg_last5 = sum(HomeGamesToSum_last5$sat_for)/nrow(HomeGamesToSum_last5)
    ,home_sat_against_avg_last5 = sum(HomeGamesToSum_last5$sat_against)/nrow(HomeGamesToSum_last5)
    ,home_sat_avg_last5 = sum(HomeGamesToSum_last5$sat)/nrow(HomeGamesToSum_last5)
    ,home_sat_total_last5 = sum(HomeGamesToSum_last5$sat)
    ,home_sat_tied_avg_last5 = sum(HomeGamesToSum_last5$sat_tied)/nrow(HomeGamesToSum_last5)
    ,home_sat_tied_total_last5 = sum(HomeGamesToSum_last5$sat_tied)
    ,home_sat_ahead_avg_last5 = sum(HomeGamesToSum_last5$sat_ahead)/nrow(HomeGamesToSum_last5)
    ,home_sat_ahead_total_last5 = sum(HomeGamesToSum_last5$sat_ahead)
    ,home_sat_behind_avg_last5 = sum(HomeGamesToSum_last5$sat_behind)/nrow(HomeGamesToSum_last5)
    ,home_sat_behind_total_last5 = sum(HomeGamesToSum_last5$sat_behind)
    ,home_sat_close_avg_last5 = sum(HomeGamesToSum_last5$sat_close)/nrow(HomeGamesToSum_last5)
    ,home_sat_close_total_last5 = sum(HomeGamesToSum_last5$sat_close)
    ,home_usat_for_avg_last5 = sum(HomeGamesToSum_last5$usat_for)/nrow(HomeGamesToSum_last5)
    ,home_usat_against_avg_last5 = sum(HomeGamesToSum_last5$usat_agst)/nrow(HomeGamesToSum_last5)
    ,home_usat_avg_last5 = sum(HomeGamesToSum_last5$usat)/nrow(HomeGamesToSum_last5)
    ,home_usat_total_last5 = sum(HomeGamesToSum_last5$usat)
    ,home_usat_tied_avg_last5 = sum(HomeGamesToSum_last5$usat_tied)/nrow(HomeGamesToSum_last5)
    ,home_usat_tied_total_last5 = sum(HomeGamesToSum_last5$usat_tied)
    ,home_usat_ahead_avg_last5 = sum(HomeGamesToSum_last5$usat_ahead)/nrow(HomeGamesToSum_last5)
    ,home_usat_ahead_total_last5 = sum(HomeGamesToSum_last5$usat_ahead)
    ,home_usat_behind_avg_last5 = sum(HomeGamesToSum_last5$usat_behind)/nrow(HomeGamesToSum_last5)
    ,home_usat_behind_total_last5 = sum(HomeGamesToSum_last5$usat_behind)
    ,home_usat_close_avg_last5 = sum(HomeGamesToSum_last5$usat_close)/nrow(HomeGamesToSum_last5)
    ,home_usat_close_total_last5 = sum(HomeGamesToSum_last5$usat_close)
    ,home_gf_avg_last5 = sum(HomeGamesToSum_last5$gf)/nrow(HomeGamesToSum_last5)
    ,home_ga_avg_last5 = sum(HomeGamesToSum_last5$ga)/nrow(HomeGamesToSum_last5)
    ,home_goal_diff_avg_last5 = sum(HomeGamesToSum_last5$gf - HomeGamesToSum_last5$ga) / nrow(HomeGamesToSum_last5)
    ,home_goal_diff_total_last5 = sum(HomeGamesToSum_last5$gf - HomeGamesToSum_last5$ga)
    ,home_ev_gf_avg_last5 = sum(HomeGamesToSum_last5$ev_gf)/nrow(HomeGamesToSum_last5)
    ,home_ev_ga_avg_last5 = sum(HomeGamesToSum_last5$ev_ga)/nrow(HomeGamesToSum_last5)
    ,home_ev_goal_diff_avg_last5 = sum(HomeGamesToSum_last5$ev_gf - HomeGamesToSum_last5$ev_ga) / nrow(HomeGamesToSum_last5)
    ,home_ev_goal_diff_total_last5 = sum(HomeGamesToSum_last5$ev_gf - HomeGamesToSum_last5$ev_ga)
    ,home_pp_gf_avg_last5 = sum(HomeGamesToSum_last5$pp_gf)/nrow(HomeGamesToSum_last5)
    ,home_pp_ga_avg_last5 = sum(HomeGamesToSum_last5$pp_ga)/nrow(HomeGamesToSum_last5)
    ,home_pp_goal_diff_avg_last5 = sum(HomeGamesToSum_last5$pp_gf - HomeGamesToSum_last5$pp_ga) / nrow(HomeGamesToSum_last5)
    ,home_pp_goal_diff_total_last5 = sum(HomeGamesToSum_last5$pp_gf - HomeGamesToSum_last5$pp_ga)
    ,home_sh_gf_avg_last5 = sum(HomeGamesToSum_last5$sh_gf)/nrow(HomeGamesToSum_last5)
    ,home_sh_ga_avg_last5 = sum(HomeGamesToSum_last5$sh_ga)/nrow(HomeGamesToSum_last5)
    ,home_sh_goal_diff_avg_last5 = sum(HomeGamesToSum_last5$sh_gf - HomeGamesToSum_last5$sh_ga) / nrow(HomeGamesToSum_last5)
    ,home_sh_goal_diff_total_last5 = sum(HomeGamesToSum_last5$sh_gf - HomeGamesToSum_last5$sh_ga)
    ,home_gf_in_p1_avg_last5 = sum(HomeGamesToSum_last5$gf_in_p1)/nrow(HomeGamesToSum_last5)
    ,home_ga_in_p1_avg_last5 = sum(HomeGamesToSum_last5$ga_in_p1)/nrow(HomeGamesToSum_last5)
    ,home_goal_in_p1_diff_avg_last5 = sum(HomeGamesToSum_last5$gf_in_p1 - HomeGamesToSum_last5$ga_in_p1) / nrow(HomeGamesToSum_last5)
    ,home_goal_in_p1_diff_total_last5 = sum(HomeGamesToSum_last5$gf_in_p1 - HomeGamesToSum_last5$ga_in_p1)
    ,home_gf_in_p2_avg_last5 = sum(HomeGamesToSum_last5$gf_in_p2)/nrow(HomeGamesToSum_last5)
    ,home_ga_in_p2_avg_last5 = sum(HomeGamesToSum_last5$ga_in_p2)/nrow(HomeGamesToSum_last5)
    ,home_goal_in_p2_diff_avg_last5 = sum(HomeGamesToSum_last5$gf_in_p2 - HomeGamesToSum_last5$ga_in_p2) / nrow(HomeGamesToSum_last5)
    ,home_goal_in_p2_diff_total_last5 = sum(HomeGamesToSum_last5$gf_in_p2 - HomeGamesToSum_last5$ga_in_p2)
    ,home_gf_in_p3_avg_last5 = sum(HomeGamesToSum_last5$gf_in_p3)/nrow(HomeGamesToSum_last5)
    ,home_ga_in_p3_avg_last5 = sum(HomeGamesToSum_last5$ga_in_p3)/nrow(HomeGamesToSum_last5)
    ,home_goal_in_p3_diff_avg_last5 = sum(HomeGamesToSum_last5$gf_in_p3 - HomeGamesToSum_last5$ga_in_p3) / nrow(HomeGamesToSum_last5)
    ,home_goal_in_p3_diff_total_last5 = sum(HomeGamesToSum_last5$gf_in_p3 - HomeGamesToSum_last5$ga_in_p3)
    ,home_gf_in_ot_avg_last5 = sum(HomeGamesToSum_last5$gf_in_ot)/nrow(HomeGamesToSum_last5)
    ,home_ga_in_ot_avg_last5 = sum(HomeGamesToSum_last5$ga_in_ot)/nrow(HomeGamesToSum_last5)
    ,home_goal_in_ot_diff_avg_last5 = sum(HomeGamesToSum_last5$gf_in_ot - HomeGamesToSum_last5$ga_in_ot) / nrow(HomeGamesToSum_last5)
    ,home_goal_in_ot_diff_total_last5 = sum(HomeGamesToSum_last5$gf_in_ot - HomeGamesToSum_last5$ga_in_ot)
    ,home_5v5_TOI_avg_last5 = sum(HomeGamesToSum_last5$`5v5_TOI`) / nrow(HomeGamesToSum_last5)
    ,home_hits_for_avg_last5 = sum(HomeGamesToSum_last5$hits_for)/nrow(HomeGamesToSum_last5)
    ,home_hits_agst_avg_last5 = sum(HomeGamesToSum_last5$hits_agst)/nrow(HomeGamesToSum_last5)
    ,home_hits_diff_avg_last5 = sum(HomeGamesToSum_last5$hits_for - HomeGamesToSum_last5$hits_agst) / nrow(HomeGamesToSum_last5)
    ,home_hits_diff_total_last5 = sum(HomeGamesToSum_last5$hits_for - HomeGamesToSum_last5$hits_agst)
    ,home_blks_for_avg_last5 = sum(HomeGamesToSum_last5$blks_for)/nrow(HomeGamesToSum_last5)
    ,home_blks_agst_avg_last5 = sum(HomeGamesToSum_last5$blks_agst)/nrow(HomeGamesToSum_last5)
    ,home_blks_diff_avg_last5 = sum(HomeGamesToSum_last5$blks_for - HomeGamesToSum_last5$blks_agst) / nrow(HomeGamesToSum_last5)
    ,home_blks_diff_total_last5 = sum(HomeGamesToSum_last5$blks_for - HomeGamesToSum_last5$blks_agst)
    ,home_GvA_avg_last5 = sum(HomeGamesToSum_last5$GvA)/nrow(HomeGamesToSum_last5)
    ,home_TkA_avg_last5 = sum(HomeGamesToSum_last5$TkA)/nrow(HomeGamesToSum_last5)
    ,home_ENG_avg_last5 = sum(HomeGamesToSum_last5$ENG)/nrow(HomeGamesToSum_last5)
    ,home_ENG_opp_avg_last5 = sum(HomeGamesToSum_last5$ENG_opp)/nrow(HomeGamesToSum_last5)
    ,home_MsS_avg_last5 = sum(HomeGamesToSum_last5$MsS)/nrow(HomeGamesToSum_last5)
    ,home_PP_Opp_avg_last5 = sum(HomeGamesToSum_last5$PP_Opp)/nrow(HomeGamesToSum_last5)
    ,`home_PP%_last5` = sum(HomeGamesToSum_last5$pp_gf) / sum(HomeGamesToSum_last5$PP_Opp)
    ,home_PP_Opp_agnst_avg_last5 = sum(HomeGamesToSum_last5$PP_Opp_Agnst)/nrow(HomeGamesToSum_last5)
    ,`home_PenatlyKill%_last5` = 1- (sum(HomeGamesToSum_last5$pp_ga) / sum(HomeGamesToSum_last5$PP_Opp_Agnst))
    ,home_W_last5 = sum(HomeGamesToSum_last5$W)
    ,home_L_last5 = sum(HomeGamesToSum_last5$L)
    ,home_OT_last5 = sum(HomeGamesToSum_last5$OT)
    ,home_Pts_last5 = (2 * home_W_last5) + home_OT_last5
    ,`home_Pt%_last5` = home_Pts_last5 / (2*nrow(HomeGamesToSum_last5))
    ,home_SO_last5 = sum(HomeGamesToSum_last5$SO)
    ,home_OT_win_last5 = sum(HomeGamesToSum_last5$OT_win)
    
    
     )
  
  
   AwayGamesToSum_last5 <- TeamGameStats %>% filter(FocusTeam == selectedgame$AwayTeam
                                                    #, GameNumber < selectedgame$AwayGameNumber
                                                    , GameNumber >= max(AwayGamesToSum$GameNumber) - 4
                                                      #selectedgame$AwayGameNumber - 5
                                                    ,Season == selectedgame$Season)
   
   
   AwayPastStats_last5 <- AwayPastStats_last5 %>% mutate(
    away_fo_avg_last5 = sum(AwayGamesToSum_last5$fo)/ nrow(AwayGamesToSum_last5)
    ,away_fow_avg_last5 = sum(AwayGamesToSum_last5$fow)/ nrow(AwayGamesToSum_last5)
    ,away_fol_avg_last5 = sum(AwayGamesToSum_last5$fol)/ nrow(AwayGamesToSum_last5)
    ,`away_fow%_last5` = sum(AwayGamesToSum_last5$fow)/sum(AwayGamesToSum_last5$fo)
    ,away_ev_fo_avg_last5 = sum(AwayGamesToSum_last5$ev_fo)/ nrow(AwayGamesToSum_last5)
    ,away_ev_fow_avg_last5 = sum(AwayGamesToSum_last5$ev_fow)/ nrow(AwayGamesToSum_last5)
    ,away_ev_fol_avg_last5 = sum(AwayGamesToSum_last5$ev_fol)/ nrow(AwayGamesToSum_last5)
    ,`away_ev_fow%_last5` = sum(AwayGamesToSum_last5$ev_fow)/sum(AwayGamesToSum_last5$ev_fo)
    ,away_pp_fo_avg_last5 = sum(AwayGamesToSum_last5$pp_fo)/ nrow(AwayGamesToSum_last5)
    ,away_pp_fow_avg_last5 = sum(AwayGamesToSum_last5$pp_fow)/ nrow(AwayGamesToSum_last5)
    ,away_pp_fol_avg_last5 = sum(AwayGamesToSum_last5$pp_fol)/ nrow(AwayGamesToSum_last5)
    ,`away_pp_fow%_last5` = sum(AwayGamesToSum_last5$pp_fow)/sum(AwayGamesToSum_last5$pp_fo)
    ,away_sh_fo_avg_last5 = sum(AwayGamesToSum_last5$sh_fo)/ nrow(AwayGamesToSum_last5)
    ,away_sh_fow_avg_last5 = sum(AwayGamesToSum_last5$sh_fow)/ nrow(AwayGamesToSum_last5)
    ,away_sh_fol_avg_last5 = sum(AwayGamesToSum_last5$sh_fol)/ nrow(AwayGamesToSum_last5)
    ,`away_sh_fow%_last5` = sum(AwayGamesToSum_last5$sh_fow)/sum(AwayGamesToSum_last5$sh_fo)
    ,away_oz_fo_avg_last5 = sum(AwayGamesToSum_last5$oz_fo)/ nrow(AwayGamesToSum_last5)
    ,away_oz_fow_avg_last5 = sum(AwayGamesToSum_last5$oz_fow)/ nrow(AwayGamesToSum_last5)
    ,away_oz_fol_avg_last5 = sum(AwayGamesToSum_last5$oz_fol)/ nrow(AwayGamesToSum_last5)
    ,`away_oz_fow%_last5` = sum(AwayGamesToSum_last5$oz_fow)/sum(AwayGamesToSum_last5$oz_fo)
    ,away_nz_fo_avg_last5 = sum(AwayGamesToSum_last5$nz_fo)/ nrow(AwayGamesToSum_last5)
    ,away_nz_fow_avg_last5 = sum(AwayGamesToSum_last5$nz_fow)/ nrow(AwayGamesToSum_last5)
    ,away_nz_fol_avg_last5 = sum(AwayGamesToSum_last5$nz_fol)/ nrow(AwayGamesToSum_last5)
    ,`away_nz_fow%_last5` = sum(AwayGamesToSum_last5$nz_fow)/sum(AwayGamesToSum_last5$nz_fo)
    ,away_dz_fo_avg_last5 = sum(AwayGamesToSum_last5$dz_fo)/ nrow(AwayGamesToSum_last5)
    ,away_dz_fow_avg_last5 = sum(AwayGamesToSum_last5$dz_fow)/ nrow(AwayGamesToSum_last5)
    ,away_dz_fol_avg_last5 = sum(AwayGamesToSum_last5$dz_fol)/ nrow(AwayGamesToSum_last5)
    ,`away_dz_fow%_last5` = sum(AwayGamesToSum_last5$dz_fow)/sum(AwayGamesToSum_last5$dz_fo)
    ,away_shots_avg_last5 = sum(AwayGamesToSum_last5$shots)/nrow(AwayGamesToSum_last5)
    ,away_shots_against_avg_last5 = sum(AwayGamesToSum_last5$shots_against)/nrow(AwayGamesToSum_last5)
    ,away_sat_for_avg_last5 = sum(AwayGamesToSum_last5$sat_for)/nrow(AwayGamesToSum_last5)
    ,away_sat_against_avg_last5 = sum(AwayGamesToSum_last5$sat_against)/nrow(AwayGamesToSum_last5)
    ,away_sat_avg_last5 = sum(AwayGamesToSum_last5$sat)/nrow(AwayGamesToSum_last5)
    ,away_sat_total_last5 = sum(AwayGamesToSum_last5$sat)
    ,away_sat_tied_avg_last5 = sum(AwayGamesToSum_last5$sat_tied)/nrow(AwayGamesToSum_last5)
    ,away_sat_tied_total_last5 = sum(AwayGamesToSum_last5$sat_tied)
    ,away_sat_ahead_avg_last5 = sum(AwayGamesToSum_last5$sat_ahead)/nrow(AwayGamesToSum_last5)
    ,away_sat_ahead_total_last5 = sum(AwayGamesToSum_last5$sat_ahead)
    ,away_sat_behind_avg_last5 = sum(AwayGamesToSum_last5$sat_behind)/nrow(AwayGamesToSum_last5)
    ,away_sat_behind_total_last5 = sum(AwayGamesToSum_last5$sat_behind)
    ,away_sat_close_avg_last5 = sum(AwayGamesToSum_last5$sat_close)/nrow(AwayGamesToSum_last5)
    ,away_sat_close_total_last5 = sum(AwayGamesToSum_last5$sat_close)
    ,away_usat_for_avg_last5 = sum(AwayGamesToSum_last5$usat_for)/nrow(AwayGamesToSum_last5)
    ,away_usat_against_avg_last5 = sum(AwayGamesToSum_last5$usat_agst)/nrow(AwayGamesToSum_last5)
    ,away_usat_avg_last5 = sum(AwayGamesToSum_last5$usat)/nrow(AwayGamesToSum_last5)
    ,away_usat_total_last5 = sum(AwayGamesToSum_last5$usat)
    ,away_usat_tied_avg_last5 = sum(AwayGamesToSum_last5$usat_tied)/nrow(AwayGamesToSum_last5)
    ,away_usat_tied_total_last5 = sum(AwayGamesToSum_last5$usat_tied)
    ,away_usat_ahead_avg_last5 = sum(AwayGamesToSum_last5$usat_ahead)/nrow(AwayGamesToSum_last5)
    ,away_usat_ahead_total_last5 = sum(AwayGamesToSum_last5$usat_ahead)
    ,away_usat_behind_avg_last5 = sum(AwayGamesToSum_last5$usat_behind)/nrow(AwayGamesToSum_last5)
    ,away_usat_behind_total_last5 = sum(AwayGamesToSum_last5$usat_behind)
    ,away_usat_close_avg_last5 = sum(AwayGamesToSum_last5$usat_close)/nrow(AwayGamesToSum_last5)
    ,away_usat_close_total_last5 = sum(AwayGamesToSum_last5$usat_close)
    ,away_gf_avg_last5 = sum(AwayGamesToSum_last5$gf)/nrow(AwayGamesToSum_last5)
    ,away_ga_avg_last5 = sum(AwayGamesToSum_last5$ga)/nrow(AwayGamesToSum_last5)
    ,away_goal_diff_avg_last5 = sum(AwayGamesToSum_last5$gf - AwayGamesToSum_last5$ga) / nrow(AwayGamesToSum_last5)
    ,away_goal_diff_total_last5 = sum(AwayGamesToSum_last5$gf - AwayGamesToSum_last5$ga)
    ,away_ev_gf_avg_last5 = sum(AwayGamesToSum_last5$ev_gf)/nrow(AwayGamesToSum_last5)
    ,away_ev_ga_avg_last5 = sum(AwayGamesToSum_last5$ev_ga)/nrow(AwayGamesToSum_last5)
    ,away_ev_goal_diff_avg_last5 = sum(AwayGamesToSum_last5$ev_gf - AwayGamesToSum_last5$ev_ga) / nrow(AwayGamesToSum_last5)
    ,away_ev_goal_diff_total_last5 = sum(AwayGamesToSum_last5$ev_gf - AwayGamesToSum_last5$ev_ga)
    ,away_pp_gf_avg_last5 = sum(AwayGamesToSum_last5$pp_gf)/nrow(AwayGamesToSum_last5)
    ,away_pp_ga_avg_last5 = sum(AwayGamesToSum_last5$pp_ga)/nrow(AwayGamesToSum_last5)
    ,away_pp_goal_diff_avg_last5 = sum(AwayGamesToSum_last5$pp_gf - AwayGamesToSum_last5$pp_ga) / nrow(AwayGamesToSum_last5)
    ,away_pp_goal_diff_total_last5 = sum(AwayGamesToSum_last5$pp_gf - AwayGamesToSum_last5$pp_ga)
    ,away_sh_gf_avg_last5 = sum(AwayGamesToSum_last5$sh_gf)/nrow(AwayGamesToSum_last5)
    ,away_sh_ga_avg_last5 = sum(AwayGamesToSum_last5$sh_ga)/nrow(AwayGamesToSum_last5)
    ,away_sh_goal_diff_avg_last5 = sum(AwayGamesToSum_last5$sh_gf - AwayGamesToSum_last5$sh_ga) / nrow(AwayGamesToSum_last5)
    ,away_sh_goal_diff_total_last5 = sum(AwayGamesToSum_last5$sh_gf - AwayGamesToSum_last5$sh_ga)
    ,away_gf_in_p1_avg_last5 = sum(AwayGamesToSum_last5$gf_in_p1)/nrow(AwayGamesToSum_last5)
    ,away_ga_in_p1_avg_last5 = sum(AwayGamesToSum_last5$ga_in_p1)/nrow(AwayGamesToSum_last5)
    ,away_goal_in_p1_diff_avg_last5 = sum(AwayGamesToSum_last5$gf_in_p1 - AwayGamesToSum_last5$ga_in_p1) / nrow(AwayGamesToSum_last5)
    ,away_goal_in_p1_diff_total_last5 = sum(AwayGamesToSum_last5$gf_in_p1 - AwayGamesToSum_last5$ga_in_p1)
    ,away_gf_in_p2_avg_last5 = sum(AwayGamesToSum_last5$gf_in_p2)/nrow(AwayGamesToSum_last5)
    ,away_ga_in_p2_avg_last5 = sum(AwayGamesToSum_last5$ga_in_p2)/nrow(AwayGamesToSum_last5)
    ,away_goal_in_p2_diff_avg_last5 = sum(AwayGamesToSum_last5$gf_in_p2 - AwayGamesToSum_last5$ga_in_p2) / nrow(AwayGamesToSum_last5)
    ,away_goal_in_p2_diff_total_last5 = sum(AwayGamesToSum_last5$gf_in_p2 - AwayGamesToSum_last5$ga_in_p2)
    ,away_gf_in_p3_avg_last5 = sum(AwayGamesToSum_last5$gf_in_p3)/nrow(AwayGamesToSum_last5)
    ,away_ga_in_p3_avg_last5 = sum(AwayGamesToSum_last5$ga_in_p3)/nrow(AwayGamesToSum_last5)
    ,away_goal_in_p3_diff_avg_last5 = sum(AwayGamesToSum_last5$gf_in_p3 - AwayGamesToSum_last5$ga_in_p3) / nrow(AwayGamesToSum_last5)
    ,away_goal_in_p3_diff_total_last5 = sum(AwayGamesToSum_last5$gf_in_p3 - AwayGamesToSum_last5$ga_in_p3)
    ,away_gf_in_ot_avg_last5 = sum(AwayGamesToSum_last5$gf_in_ot)/nrow(AwayGamesToSum_last5)
    ,away_ga_in_ot_avg_last5 = sum(AwayGamesToSum_last5$ga_in_ot)/nrow(AwayGamesToSum_last5)
    ,away_goal_in_ot_diff_avg_last5 = sum(AwayGamesToSum_last5$gf_in_ot - AwayGamesToSum_last5$ga_in_ot) / nrow(AwayGamesToSum_last5)
    ,away_goal_in_ot_diff_total_last5 = sum(AwayGamesToSum_last5$gf_in_ot - AwayGamesToSum_last5$ga_in_ot)
    ,away_5v5_TOI_avg_last5 = sum(AwayGamesToSum_last5$`5v5_TOI`) / nrow(AwayGamesToSum_last5)
    ,away_hits_for_avg_last5 = sum(AwayGamesToSum_last5$hits_for)/nrow(AwayGamesToSum_last5)
    ,away_hits_agst_avg_last5 = sum(AwayGamesToSum_last5$hits_agst)/nrow(AwayGamesToSum_last5)
    ,away_hits_diff_avg_last5 = sum(AwayGamesToSum_last5$hits_for - AwayGamesToSum_last5$hits_agst) / nrow(AwayGamesToSum_last5)
    ,away_hits_diff_total_last5 = sum(AwayGamesToSum_last5$hits_for - AwayGamesToSum_last5$hits_agst)
    ,away_blks_for_avg_last5 = sum(AwayGamesToSum_last5$blks_for)/nrow(AwayGamesToSum_last5)
    ,away_blks_agst_avg_last5 = sum(AwayGamesToSum_last5$blks_agst)/nrow(AwayGamesToSum_last5)
    ,away_blks_diff_avg_last5 = sum(AwayGamesToSum_last5$blks_for - AwayGamesToSum_last5$blks_agst) / nrow(AwayGamesToSum_last5)
    ,away_blks_diff_total_last5 = sum(AwayGamesToSum_last5$blks_for - AwayGamesToSum_last5$blks_agst)
    ,away_GvA_avg_last5 = sum(AwayGamesToSum_last5$GvA)/nrow(AwayGamesToSum_last5)
    ,away_TkA_avg_last5 = sum(AwayGamesToSum_last5$TkA)/nrow(AwayGamesToSum_last5)
    ,away_ENG_avg_last5 = sum(AwayGamesToSum_last5$ENG)/nrow(AwayGamesToSum_last5)
    ,away_ENG_opp_avg_last5 = sum(AwayGamesToSum_last5$ENG_opp)/nrow(AwayGamesToSum_last5)
    ,away_MsS_avg_last5 = sum(AwayGamesToSum_last5$MsS)/nrow(AwayGamesToSum_last5)
    ,away_PP_Opp_avg_last5 = sum(AwayGamesToSum_last5$PP_Opp)/nrow(AwayGamesToSum_last5)
    ,`away_PP%_last5` = sum(AwayGamesToSum_last5$pp_gf) / sum(AwayGamesToSum_last5$PP_Opp)
    ,away_PP_Opp_agnst_avg_last5 = sum(AwayGamesToSum_last5$PP_Opp_Agnst)/nrow(AwayGamesToSum_last5)
    ,`away_PenatlyKill%_last5` = 1- (sum(AwayGamesToSum_last5$pp_ga) / sum(AwayGamesToSum_last5$PP_Opp_Agnst))
    ,away_W_last5 = sum(AwayGamesToSum_last5$W)
    ,away_L_last5 = sum(AwayGamesToSum_last5$L)
    ,away_OT_last5 = sum(AwayGamesToSum_last5$OT)
    ,away_Pts_last5 = (2 * away_W_last5) + away_OT_last5
    ,`away_Pt%_last5` = away_Pts_last5 / (2*nrow(AwayGamesToSum_last5))
    ,away_SO_last5 = sum(AwayGamesToSum_last5$SO)
    ,away_OT_win_last5 = sum(AwayGamesToSum_last5$OT_win)
    
    
     )

   #bind it all together
  TotalGameStats <-  cbind(selectedgame, HomePastStats, AwayPastStats, HomePastStats_last5, AwayPastStats_last5)
   
  TotalPredictionData <- rbind(TotalPredictionData, TotalGameStats)
   
}

#remove duplicate column names
idx = which(duplicated(names(TotalPredictionData)))

TotalPredictionData = TotalPredictionData[,-idx]

TotalPredictionData_Final <- TotalPredictionData %>% mutate(Year = year(Date)
                               ,Month = month(Date)
                               ,Day = day(Date)
                               ,SeasonYearStart = as.integer(substr(Season, start = 1, stop = 4)))

#Manually One-Hot Encode teams since not all are in this dataset
TotalPredictionData_Final <- TotalPredictionData_Final %>% mutate(
  HomeTeamAnaheim.Ducks = case_when(HomeTeam == "Anaheim Ducks" ~ 1, HomeTeam != "Anaheim Ducks" ~ 0)
  ,HomeTeamArizona.Coyotes = case_when(HomeTeam == "Arizona Coyotes" | HomeTeam =="Utah Hockey Club" ~ 1, HomeTeam != "Arizona Coyotes" | HomeTeam !="Utah Hockey Club" ~ 0)
  ,HomeTeamBoston.Bruins = case_when(HomeTeam == "Boston Bruins" ~ 1, HomeTeam != "Boston Bruins" ~ 0)
  ,HomeTeamBuffalo.Sabres = case_when(HomeTeam == "Buffalo Sabres" ~ 1, HomeTeam != "Buffalo Sabres" ~ 0)
  ,HomeTeamCalgary.Flames = case_when(HomeTeam == "Calgary Flames" ~ 1, HomeTeam != "Calgary Flames" ~ 0)
  ,HomeTeamCarolina.Hurricanes = case_when(HomeTeam == "Carolina Hurricanes" ~ 1, HomeTeam != "Carolina Hurricanes" ~ 0)
  ,HomeTeamChicago.Blackhawks = case_when(HomeTeam == "Chicago Blackhawks" ~ 1, HomeTeam != "Chicago Blackhawks" ~ 0)
  ,HomeTeamColorado.Avalanche = case_when(HomeTeam == "Colorado Avalanche " ~ 1, HomeTeam != "Colorado Avalanche " ~ 0)
  ,HomeTeamColumbus.Blue.Jackets = case_when(HomeTeam == "Columbus Blue Jackets" ~ 1, HomeTeam != "Columbus Blue Jackets" ~ 0)
  ,HomeTeamDallas.Stars = case_when(HomeTeam == "Dallas Stars" ~ 1, HomeTeam != "Dallas Stars" ~ 0)
  ,HomeTeamDetroit.Red.Wings = case_when(HomeTeam == "Detroit Red Wings" ~ 1, HomeTeam != "Detroit Red Wings" ~ 0)
  ,HomeTeamEdmonton.Oilers = case_when(HomeTeam == "Edmonton Oilers" ~ 1, HomeTeam != "Edmonton Oilers" ~ 0)
  ,HomeTeamFlorida.Panthers = case_when(HomeTeam == "Florida Panthers" ~ 1, HomeTeam != "Florida Panthers" ~ 0)
  ,HomeTeamLos.Angeles.Kings = case_when(HomeTeam == "Los Angeles Kings" ~ 1, HomeTeam != "Los Angeles Kings" ~ 0)
  ,HomeTeamMinnesota.Wild = case_when(HomeTeam == "Minnesota Wild" ~ 1, HomeTeam != "Minnesota Wild" ~ 0)
  ,HomeTeamMontréal.Canadiens = case_when(HomeTeam == "Montréal Canadiens" ~ 1, HomeTeam != "Montréal Canadiens" ~ 0)
  ,HomeTeamNashville.Predators = case_when(HomeTeam == "Nashville Predators" ~ 1, HomeTeam != "Nashville Predators" ~ 0)
  ,HomeTeamNew.Jersey.Devils = case_when(HomeTeam == "New Jersey Devils" ~ 1, HomeTeam != "New Jersey Devils" ~ 0)
  ,HomeTeamNew.York.Islanders = case_when(HomeTeam == "New York Islanders" ~ 1, HomeTeam != "New York Islanders" ~ 0)
  ,HomeTeamNew.York.Rangers = case_when(HomeTeam == "New York Rangers" ~ 1, HomeTeam != "New York Rangers" ~ 0)
  ,HomeTeamOttawa.Senators = case_when(HomeTeam == "Ottawa Senators" ~ 1, HomeTeam != "Ottawa Senators" ~ 0)
  ,HomeTeamPhiladelphia.Flyers = case_when(HomeTeam == "Philadelphia Flyers" ~ 1, HomeTeam != "Philadelphia Flyers" ~ 0)
  ,HomeTeamPittsburgh.Penguins = case_when(HomeTeam == "Pittsburgh Penguins" ~ 1, HomeTeam != "Pittsburgh Penguins" ~ 0)
  ,HomeTeamSan.Jose.Sharks = case_when(HomeTeam == "San Jose Sharks" ~ 1, HomeTeam != "San Jose Sharks" ~ 0)
  ,HomeTeamSeattle.Kraken = case_when(HomeTeam == "Seattle Kraken" ~ 1, HomeTeam != "Seattle Kraken" ~ 0)
  ,HomeTeamSt..Louis.Blues = case_when(HomeTeam == "St. Louis Blues" ~ 1, HomeTeam != "St. Louis Blues" ~ 0)
  ,HomeTeamTampa.Bay.Lightning = case_when(HomeTeam == "Tampa Bay Lightning" ~ 1, HomeTeam != "Tampa Bay Lightning" ~ 0)
  ,HomeTeamToronto.Maple.Leafs = case_when(HomeTeam == "Toronto Maple Leafs" ~ 1, HomeTeam != "Toronto Maple Leafs" ~ 0)
  ,HomeTeamVancouver.Canucks = case_when(HomeTeam == "Vancouver Canucks" ~ 1, HomeTeam != "Vancouver Canucks" ~ 0)
  ,HomeTeamVegas.Golden.Knights = case_when(HomeTeam == "Vegas Golden Knights" ~ 1, HomeTeam != "Vegas Golden Knights" ~ 0)
  ,HomeTeamWashington.Capitals = case_when(HomeTeam == "Washington Capitals" ~ 1, HomeTeam != "Washington Capitals" ~ 0)
  ,HomeTeamWinnipeg.Jets = case_when(HomeTeam == "Winnipeg Jets" ~ 1, HomeTeam != "Winnipeg Jets" ~ 0)
  ,AwayTeamAnaheim.Ducks = case_when(AwayTeam == "Anaheim Ducks" ~ 1, AwayTeam != "Anaheim Ducks" ~ 0)
  ,AwayTeamArizona.Coyotes = case_when(AwayTeam == "Arizona Coyotes" | AwayTeam =="Utah Hockey Club" ~ 1, AwayTeam != "Arizona Coyotes" | AwayTeam !="Utah Hockey Club" ~ 0)
  ,AwayTeamBoston.Bruins = case_when(AwayTeam == "Boston Bruins" ~ 1, AwayTeam != "Boston Bruins" ~ 0)
  ,AwayTeamBuffalo.Sabres = case_when(AwayTeam == "Buffalo Sabres" ~ 1, AwayTeam != "Buffalo Sabres" ~ 0)
  ,AwayTeamCalgary.Flames = case_when(AwayTeam == "Calgary Flames" ~ 1, AwayTeam != "Calgary Flames" ~ 0)
  ,AwayTeamCarolina.Hurricanes = case_when(AwayTeam == "Carolina Hurricanes" ~ 1, AwayTeam != "Carolina Hurricanes" ~ 0)
  ,AwayTeamChicago.Blackhawks = case_when(AwayTeam == "Chicago Blackhawks" ~ 1, AwayTeam != "Chicago Blackhawks" ~ 0)
  ,AwayTeamColorado.Avalanche = case_when(AwayTeam == "Colorado.Avalanche" ~ 1, AwayTeam != "Colorado.Avalanche" ~ 0)
  ,AwayTeamColumbus.Blue.Jackets = case_when(AwayTeam == "Columbus Blue Jackets" ~ 1, AwayTeam != "Columbus Blue Jackets" ~ 0)
  ,AwayTeamDallas.Stars = case_when(AwayTeam == "Dallas Stars" ~ 1, AwayTeam != "Dallas Stars" ~ 0)
  ,AwayTeamDetroit.Red.Wings = case_when(AwayTeam == "Detroit Red Wings" ~ 1, AwayTeam != "Detroit Red Wings" ~ 0)
  ,AwayTeamEdmonton.Oilers = case_when(AwayTeam == "Edmonton Oilers" ~ 1, AwayTeam != "Edmonton Oilers" ~ 0)
  ,AwayTeamFlorida.Panthers = case_when(AwayTeam == "Florida Panthers" ~ 1, AwayTeam != "Florida Panthers" ~ 0)
  ,AwayTeamLos.Angeles.Kings = case_when(AwayTeam == "Los Angeles Kings" ~ 1, AwayTeam != "Los Angeles Kings" ~ 0)
  ,AwayTeamMinnesota.Wild = case_when(AwayTeam == "Minnesota Wild" ~ 1, AwayTeam != "Minnesota Wild" ~ 0)
  ,AwayTeamMontréal.Canadiens = case_when(AwayTeam == "Montréal Canadiens" ~ 1, AwayTeam != "Montréal Canadiens" ~ 0)
  ,AwayTeamNashville.Predators = case_when(AwayTeam == "Nashville Predators" ~ 1, AwayTeam != "Nashville Predators" ~ 0)
  ,AwayTeamNew.Jersey.Devils = case_when(AwayTeam == "New Jersey Devils" ~ 1, AwayTeam != "New Jersey Devils" ~ 0)
  ,AwayTeamNew.York.Islanders = case_when(AwayTeam == "New York Islanders" ~ 1, AwayTeam != "New York Islanders" ~ 0)
  ,AwayTeamNew.York.Rangers = case_when(AwayTeam == "New York Rangers" ~ 1, AwayTeam != "New York Rangers" ~ 0)
  ,AwayTeamOttawa.Senators = case_when(AwayTeam == "Ottawa Senators" ~ 1, AwayTeam != "Ottawa Senators" ~ 0)
  ,AwayTeamPhiladelphia.Flyers = case_when(AwayTeam == "Philadelphia Flyers" ~ 1, AwayTeam != "Philadelphia Flyers" ~ 0)
  ,AwayTeamPittsburgh.Penguins = case_when(AwayTeam == "Pittsburgh Penguins" ~ 1, AwayTeam != "Pittsburgh Penguins" ~ 0)
  ,AwayTeamSan.Jose.Sharks = case_when(AwayTeam == "San Jose Sharks" ~ 1, AwayTeam != "San Jose Sharks" ~ 0)
  ,AwayTeamSeattle.Kraken = case_when(AwayTeam == "Seattle Kraken" ~ 1, AwayTeam != "Seattle Kraken" ~ 0)
  ,AwayTeamSt..Louis.Blues = case_when(AwayTeam == "St. Louis Blues" ~ 1, AwayTeam != "St. Louis Blues" ~ 0)
  ,AwayTeamTampa.Bay.Lightning = case_when(AwayTeam == "Tampa Bay Lightning" ~ 1, AwayTeam != "Tampa Bay Lightning" ~ 0)
  ,AwayTeamToronto.Maple.Leafs = case_when(AwayTeam == "Toronto Maple Leafs" ~ 1, AwayTeam != "Toronto Maple Leafs" ~ 0)
  ,AwayTeamVancouver.Canucks = case_when(AwayTeam == "Vancouver Canucks" ~ 1, AwayTeam != "Vancouver Canucks" ~ 0)
  ,AwayTeamVegas.Golden.Knights = case_when(AwayTeam == "Vegas Golden Knights" ~ 1, AwayTeam != "Vegas Golden Knights" ~ 0)
  ,AwayTeamWashington.Capitals = case_when(AwayTeam == "Washington Capitals" ~ 1, AwayTeam != "Washington Capitals" ~ 0)
  ,AwayTeamWinnipeg.Jets = case_when(AwayTeam == "Winnipeg Jets" ~ 1, AwayTeam != "Winnipeg Jets" ~ 0)
)

#subtract home vs away to get a combined informative stat
TotalPredictionData_Final_v2 <- TotalPredictionData_Final %>% mutate(
  fo_avg_diff = home_fo_avg - away_fo_avg
  ,fow_avg_diff = home_fow_avg - away_fow_avg
  ,fol_avg_diff = home_fol_avg - away_fol_avg
  ,`fow%_diff` = `home_fow%` - `away_fow%`
  ,ev_fo_avg_diff = home_ev_fo_avg - away_ev_fo_avg
  ,ev_fow_avg_diff = home_ev_fow_avg - away_ev_fow_avg
  ,ev_fol_avg_diff = home_ev_fol_avg - away_ev_fol_avg
  ,`ev_fow%_diff` = `home_ev_fow%` - `away_ev_fow%`
  ,pp_fo_avg_diff = home_pp_fo_avg - away_pp_fo_avg
  ,pp_fow_avg_diff = home_pp_fow_avg - away_pp_fow_avg
  ,pp_fol_avg_diff = home_pp_fol_avg - away_pp_fol_avg
  ,`pp_fow%_diff` = `home_pp_fow%` - `away_pp_fow%`
  ,sh_fo_avg_diff = home_sh_fo_avg - away_sh_fo_avg
  ,sh_fow_avg_diff = home_sh_fow_avg - away_sh_fow_avg
  ,sh_fol_avg_diff = home_sh_fol_avg - away_sh_fol_avg
  ,`sh_fow%_diff` = `home_sh_fow%` - `away_sh_fow%`
  ,oz_fo_avg_diff = home_oz_fo_avg - away_oz_fo_avg
  ,oz_fow_avg_diff = home_oz_fow_avg - away_oz_fow_avg
  ,oz_fol_avg_diff = home_oz_fol_avg - away_oz_fol_avg
  ,`oz_fow%_diff` = `home_oz_fow%` - `away_oz_fow%`
  ,nz_fo_avg_diff = home_nz_fo_avg - away_nz_fo_avg
  ,nz_fow_avg_diff = home_nz_fow_avg - away_nz_fow_avg
  ,nz_fol_avg_diff = home_nz_fol_avg - away_nz_fol_avg
  ,`nz_fow%_diff` = `home_nz_fow%` - `away_nz_fow%`
  ,dz_fo_avg_diff = home_dz_fo_avg - away_dz_fo_avg
  ,dz_fow_avg_diff = home_dz_fow_avg - away_dz_fow_avg
  ,dz_fol_avg_diff = home_dz_fol_avg - away_dz_fol_avg
  ,`dz_fow%_diff` = `home_dz_fow%` - `away_dz_fow%`
  ,shots_avg_diff = home_shots_avg - away_shots_avg
  ,shots_against_avg_diff = home_shots_against_avg - away_shots_against_avg
  ,sat_for_avg_diff = home_sat_for_avg - away_sat_for_avg
  ,sat_against_avg_diff = home_sat_against_avg - away_sat_against_avg
  ,sat_avg_diff = home_sat_avg - away_sat_avg
  ,sat_total_diff = home_sat_total - away_sat_total
  ,sat_tied_avg_diff = home_sat_tied_avg - away_sat_tied_avg
  ,sat_tied_total_diff = home_sat_tied_total - away_sat_tied_total
  ,sat_ahead_avg_diff = home_sat_ahead_avg - away_sat_ahead_avg
  ,sat_ahead_total_diff = home_sat_ahead_total - away_sat_ahead_total
  ,sat_behind_avg_diff = home_sat_behind_avg - away_sat_behind_avg
  ,sat_behind_total_diff = home_sat_behind_total - away_sat_behind_total
  ,sat_close_avg_diff = home_sat_close_avg - away_sat_close_avg
  ,sat_close_total_diff = home_sat_close_total - away_sat_close_total
  ,usat_for_avg_diff = home_usat_for_avg - away_usat_for_avg
  ,usat_against_avg_diff = home_usat_against_avg - away_usat_against_avg
  ,usat_avg_diff = home_usat_avg - away_usat_avg
  ,usat_total_diff = home_usat_total - away_usat_total
  ,usat_tied_avg_diff = home_usat_tied_avg - away_usat_tied_avg
  ,usat_tied_total_diff = home_usat_tied_total - away_usat_tied_total
  ,usat_ahead_avg_diff = home_usat_ahead_avg - away_usat_ahead_avg
  ,usat_ahead_total_diff = home_usat_ahead_total - away_usat_ahead_total
  ,usat_behind_avg_diff = home_usat_behind_avg - away_usat_behind_avg
  ,usat_behind_total_diff = home_usat_behind_total - away_usat_behind_total
  ,usat_close_avg_diff = home_usat_close_avg - away_usat_close_avg
  ,usat_close_total_diff = home_usat_close_total - away_usat_close_total
  ,gf_avg_diff = home_gf_avg - away_gf_avg
  ,ga_avg_diff = home_ga_avg - away_ga_avg
  ,goal_diff_avg_diff = home_goal_diff_avg - away_goal_diff_avg
  ,goal_diff_total_diff = home_goal_diff_total - away_goal_diff_total
  ,ev_gf_avg_diff = home_ev_gf_avg - away_ev_gf_avg
  ,ev_ga_avg_diff = home_ev_ga_avg - away_ev_ga_avg
  ,ev_goal_diff_avg_diff = home_ev_goal_diff_avg - away_ev_goal_diff_avg
  ,ev_goal_diff_total_diff = home_ev_goal_diff_total - away_ev_goal_diff_total
  ,pp_gf_avg_diff = home_pp_gf_avg - away_pp_gf_avg
  ,pp_ga_avg_diff = home_pp_ga_avg - away_pp_ga_avg
  ,pp_goal_diff_avg_diff = home_pp_goal_diff_avg - away_pp_goal_diff_avg
  ,pp_goal_diff_total_diff = home_pp_goal_diff_total - away_pp_goal_diff_total
  ,sh_gf_avg_diff = home_sh_gf_avg - away_sh_gf_avg
  ,sh_ga_avg_diff = home_sh_ga_avg - away_sh_ga_avg
  ,sh_goal_diff_avg_diff = home_sh_goal_diff_avg - away_sh_goal_diff_avg
  ,sh_goal_diff_total_diff = home_sh_goal_diff_total - away_sh_goal_diff_total
  ,gf_in_p1_avg_diff = home_gf_in_p1_avg - away_gf_in_p1_avg
  ,ga_in_p1_avg_diff = home_ga_in_p1_avg - away_ga_in_p1_avg
  ,goal_in_p1_diff_avg_diff = home_goal_in_p1_diff_avg - away_goal_in_p1_diff_avg
  ,goal_in_p1_diff_total_diff = home_goal_in_p1_diff_total - away_goal_in_p1_diff_total
  ,gf_in_p2_avg_diff = home_gf_in_p2_avg - away_gf_in_p2_avg
  ,ga_in_p2_avg_diff = home_ga_in_p2_avg - away_ga_in_p2_avg
  ,goal_in_p2_diff_avg_diff = home_goal_in_p2_diff_avg - away_goal_in_p2_diff_avg
  ,goal_in_p2_diff_total_diff = home_goal_in_p2_diff_total - away_goal_in_p2_diff_total
  ,gf_in_p3_avg_diff = home_gf_in_p3_avg - away_gf_in_p3_avg
  ,ga_in_p3_avg_diff = home_ga_in_p3_avg - away_ga_in_p3_avg
  ,goal_in_p3_diff_avg_diff = home_goal_in_p3_diff_avg - away_goal_in_p3_diff_avg
  ,goal_in_p3_diff_total_diff = home_goal_in_p3_diff_total - away_goal_in_p3_diff_total
  ,gf_in_ot_avg_diff = home_gf_in_ot_avg - away_gf_in_ot_avg
  ,ga_in_ot_avg_diff = home_ga_in_ot_avg - away_ga_in_ot_avg
  ,goal_in_ot_diff_avg_diff = home_goal_in_ot_diff_avg - away_goal_in_ot_diff_avg
  ,goal_in_ot_diff_total_diff = home_goal_in_ot_diff_total - away_goal_in_ot_diff_total
  ,`5v5_TOI_avg_diff` = home_5v5_TOI_avg - away_5v5_TOI_avg
  ,hits_for_avg_diff = home_hits_for_avg - away_hits_for_avg
  ,hits_agst_avg_diff = home_hits_agst_avg - away_hits_agst_avg
  ,hits_diff_avg_diff = home_hits_diff_avg - away_hits_diff_avg
  ,hits_diff_total_diff = home_hits_diff_total - away_hits_diff_total
  ,blks_for_avg_diff = home_blks_for_avg - away_blks_for_avg
  ,blks_agst_avg_diff = home_blks_agst_avg - away_blks_agst_avg
  ,blks_diff_avg_diff = home_blks_diff_avg - away_blks_diff_avg
  ,blks_diff_total_diff = home_blks_diff_total - away_blks_diff_total
  ,GvA_avg_diff = home_GvA_avg - away_GvA_avg
  ,TkA_avg_diff = home_TkA_avg - away_TkA_avg
  ,ENG_avg_diff = home_ENG_avg - away_ENG_avg
  ,ENG_opp_avg_diff = home_ENG_opp_avg - away_ENG_opp_avg
  ,MsS_avg_diff = home_MsS_avg - away_MsS_avg
  ,PP_Opp_avg_diff = home_PP_Opp_avg - away_PP_Opp_avg
  ,`PP%_diff` = `home_PP%` - `away_PP%`
  ,PP_Opp_agnst_avg_diff = home_PP_Opp_agnst_avg - away_PP_Opp_agnst_avg
  ,`PenaltyKill%_diff` = `home_PenatlyKill%` - `away_PenatlyKill%`
  ,W_diff = home_W - away_W
  ,L_diff = home_L - away_L
  ,OT_diff = home_OT - away_OT
  ,Pts_diff = home_Pts - away_Pts
  ,`Pt%_diff` = `home_Pt%` - `away_Pt%`
  ,SO_diff = home_SO - away_SO
  ,OT_win_diff = home_OT_win - away_OT_win
  ,days_since_last_game_diff = home_days_since_last_game - away_days_since_last_game
  ,Winning_streak_diff = home_Winning_Streak - away_Winning_Streak
  
  #last5 stats
  ,fo_avg_last5_diff = home_fo_avg_last5 - away_fo_avg_last5
  ,fow_avg_last5diff = home_fow_avg_last5 - away_fow_avg_last5
  ,fol_avg_last5_diff = home_fol_avg_last5 - away_fol_avg_last5
  ,`fow%_last5_diff` = `home_fow%_last5` - `away_fow%_last5`
  ,ev_fo_avg_last5_diff = home_ev_fo_avg_last5 - away_ev_fo_avg_last5
  ,ev_fow_avg_last5_diff = home_ev_fow_avg_last5 - away_ev_fow_avg_last5
  ,ev_fol_avg_last5_diff = home_ev_fol_avg_last5 - away_ev_fol_avg_last5
  ,`ev_fow%_last5_diff` = `home_ev_fow%_last5` - `away_ev_fow%_last5`
  ,pp_fo_avg_last5_diff = home_pp_fo_avg_last5 - away_pp_fo_avg_last5
  ,pp_fow_avg_last5_diff = home_pp_fow_avg_last5 - away_pp_fow_avg_last5
  ,pp_fol_avg_last5_diff = home_pp_fol_avg_last5 - away_pp_fol_avg_last5
  ,`pp_fow%_last5_diff` = `home_pp_fow%_last5` - `away_pp_fow%_last5`
  ,sh_fo_avg_last5_diff = home_sh_fo_avg_last5 - away_sh_fo_avg_last5
  ,sh_fow_avg_last5_diff = home_sh_fow_avg_last5 - away_sh_fow_avg_last5
  ,sh_fol_avg_last5_diff = home_sh_fol_avg_last5 - away_sh_fol_avg_last5
  ,`sh_fow%_last5_diff` = `home_sh_fow%_last5` - `away_sh_fow%_last5`
  ,oz_fo_avg_last5_diff = home_oz_fo_avg_last5 - away_oz_fo_avg_last5
  ,oz_fow_avg_last5_diff = home_oz_fow_avg_last5 - away_oz_fow_avg_last5
  ,oz_fol_avg_last5_diff = home_oz_fol_avg_last5 - away_oz_fol_avg_last5
  ,`oz_fow%_last5_diff` = `home_oz_fow%_last5` - `away_oz_fow%_last5`
  ,nz_fo_avg_last5_diff = home_nz_fo_avg_last5 - away_nz_fo_avg_last5
  ,nz_fow_avg_last5_diff = home_nz_fow_avg_last5 - away_nz_fow_avg_last5
  ,nz_fol_avg_last5_diff = home_nz_fol_avg_last5 - away_nz_fol_avg_last5
  ,`nz_fow%_last5_diff` = `home_nz_fow%_last5` - `away_nz_fow%_last5`
  ,dz_fo_avg_last5_diff = home_dz_fo_avg_last5 - away_dz_fo_avg_last5
  ,dz_fow_avg_last5_diff = home_dz_fow_avg_last5 - away_dz_fow_avg_last5
  ,dz_fol_avg_last5_diff = home_dz_fol_avg_last5 - away_dz_fol_avg_last5
  ,`dz_fow%_last5_diff` = `home_dz_fow%_last5` - `away_dz_fow%_last5`
  ,shots_avg_last5_diff = home_shots_avg_last5 - away_shots_avg_last5
  ,shots_against_avg_last5_diff = home_shots_against_avg_last5 - away_shots_against_avg_last5
  ,sat_for_avg_last5_diff = home_sat_for_avg_last5 - away_sat_for_avg_last5
  ,sat_against_avg_last5_diff = home_sat_against_avg_last5 - away_sat_against_avg_last5
  ,sat_avg_last5_diff = home_sat_avg_last5 - away_sat_avg_last5
  ,sat_total_last5_diff = home_sat_total_last5 - away_sat_total_last5
  ,sat_tied_avg_last5_diff = home_sat_tied_avg_last5 - away_sat_tied_avg_last5
  ,sat_tied_total_last5_diff = home_sat_tied_total_last5 - away_sat_tied_total_last5
  ,sat_ahead_avg_last5_diff = home_sat_ahead_avg_last5 - away_sat_ahead_avg_last5
  ,sat_ahead_total_last5_diff = home_sat_ahead_total_last5 - away_sat_ahead_total_last5
  ,sat_behind_avg_last5_diff = home_sat_behind_avg_last5 - away_sat_behind_avg_last5
  ,sat_behind_total_last5_diff = home_sat_behind_total_last5 - away_sat_behind_total_last5
  ,sat_close_avg_last5_diff = home_sat_close_avg_last5 - away_sat_close_avg_last5
  ,sat_close_total_last5_diff = home_sat_close_total_last5 - away_sat_close_total_last5
  ,usat_for_avg_last5_diff = home_usat_for_avg_last5 - away_usat_for_avg_last5
  ,usat_against_avg_last5_diff = home_usat_against_avg_last5 - away_usat_against_avg_last5
  ,usat_avg_last5_diff = home_usat_avg_last5 - away_usat_avg_last5
  ,usat_total_last5_diff = home_usat_total_last5 - away_usat_total_last5
  ,usat_tied_avg_last5_diff = home_usat_tied_avg_last5 - away_usat_tied_avg_last5
  ,usat_tied_total_last5_diff = home_usat_tied_total_last5 - away_usat_tied_total_last5
  ,usat_ahead_avg_last5_diff = home_usat_ahead_avg_last5 - away_usat_ahead_avg_last5
  ,usat_ahead_total_last5_diff = home_usat_ahead_total_last5 - away_usat_ahead_total_last5
  ,usat_behind_avg_last5_diff = home_usat_behind_avg_last5 - away_usat_behind_avg_last5
  ,usat_behind_total_last5_diff = home_usat_behind_total_last5 - away_usat_behind_total_last5
  ,usat_close_avg_last5_diff = home_usat_close_avg_last5 - away_usat_close_avg_last5
  ,usat_close_total_last5_diff = home_usat_close_total_last5 - away_usat_close_total_last5
  ,gf_avg_last5_diff = home_gf_avg_last5 - away_gf_avg_last5
  ,ga_avg_last5_diff = home_ga_avg_last5 - away_ga_avg_last5
  ,goal_diff_avg_last5_diff = home_goal_diff_avg_last5 - away_goal_diff_avg_last5
  ,goal_diff_total_last5_diff = home_goal_diff_total_last5 - away_goal_diff_total_last5
  ,ev_gf_avg_last5_diff = home_ev_gf_avg_last5 - away_ev_gf_avg_last5
  ,ev_ga_avg_last5_diff = home_ev_ga_avg_last5 - away_ev_ga_avg_last5
  ,ev_goal_diff_avg_last5_diff = home_ev_goal_diff_avg_last5 - away_ev_goal_diff_avg_last5
  ,ev_goal_diff_total_last5_diff = home_ev_goal_diff_total_last5 - away_ev_goal_diff_total_last5
  ,pp_gf_avg_last5_diff = home_pp_gf_avg_last5 - away_pp_gf_avg_last5
  ,pp_ga_avg_last5_diff = home_pp_ga_avg_last5 - away_pp_ga_avg_last5
  ,pp_goal_diff_avg_last5_diff = home_pp_goal_diff_avg_last5 - away_pp_goal_diff_avg_last5
  ,pp_goal_diff_total_last5_diff = home_pp_goal_diff_total_last5 - away_pp_goal_diff_total_last5
  ,sh_gf_avg_last5_diff = home_sh_gf_avg_last5 - away_sh_gf_avg_last5
  ,sh_ga_avg_last5_diff = home_sh_ga_avg_last5 - away_sh_ga_avg_last5
  ,sh_goal_diff_avg_last5_diff = home_sh_goal_diff_avg_last5 - away_sh_goal_diff_avg_last5
  ,sh_goal_diff_total_last5_diff = home_sh_goal_diff_total_last5 - away_sh_goal_diff_total_last5
  ,gf_in_p1_avg_last5_diff = home_gf_in_p1_avg_last5 - away_gf_in_p1_avg_last5
  ,ga_in_p1_avg_last5_diff = home_ga_in_p1_avg_last5 - away_ga_in_p1_avg_last5
  ,goal_in_p1_diff_avg_last5_diff = home_goal_in_p1_diff_avg_last5 - away_goal_in_p1_diff_avg_last5
  ,goal_in_p1_diff_total_last5_diff = home_goal_in_p1_diff_total_last5 - away_goal_in_p1_diff_total_last5
  ,gf_in_p2_avg_last5_diff = home_gf_in_p2_avg_last5 - away_gf_in_p2_avg_last5
  ,ga_in_p2_avg_last5_diff = home_ga_in_p2_avg_last5 - away_ga_in_p2_avg_last5
  ,goal_in_p2_diff_avg_last5_diff = home_goal_in_p2_diff_avg_last5 - away_goal_in_p2_diff_avg_last5
  ,goal_in_p2_diff_total_last5_diff = home_goal_in_p2_diff_total_last5 - away_goal_in_p2_diff_total_last5
  ,gf_in_p3_avg_last5_diff = home_gf_in_p3_avg_last5 - away_gf_in_p3_avg_last5
  ,ga_in_p3_avg_last5_diff = home_ga_in_p3_avg_last5 - away_ga_in_p3_avg_last5
  ,goal_in_p3_diff_avg_last5_diff = home_goal_in_p3_diff_avg_last5 - away_goal_in_p3_diff_avg_last5
  ,goal_in_p3_diff_total_last5_diff = home_goal_in_p3_diff_total_last5 - away_goal_in_p3_diff_total_last5
  ,gf_in_ot_avg_last5_diff = home_gf_in_ot_avg_last5 - away_gf_in_ot_avg_last5
  ,ga_in_ot_avg_last5_diff = home_ga_in_ot_avg_last5 - away_ga_in_ot_avg_last5
  ,goal_in_ot_diff_avg_last5_diff = home_goal_in_ot_diff_avg_last5 - away_goal_in_ot_diff_avg_last5
  ,goal_in_ot_diff_total_last5_diff = home_goal_in_ot_diff_total_last5 - away_goal_in_ot_diff_total_last5
  ,`5v5_TOI_avg_last5_diff` = home_5v5_TOI_avg_last5 - away_5v5_TOI_avg_last5
  ,hits_for_avg_last5_diff = home_hits_for_avg_last5 - away_hits_for_avg_last5
  ,hits_agst_avg_last5_diff = home_hits_agst_avg_last5 - away_hits_agst_avg_last5
  ,hits_diff_avg_last5_diff = home_hits_diff_avg_last5 - away_hits_diff_avg_last5
  ,hits_diff_total_last5_diff = home_hits_diff_total_last5 - away_hits_diff_total_last5
  ,blks_for_avg_last5_diff = home_blks_for_avg_last5 - away_blks_for_avg_last5
  ,blks_agst_avg_last5_diff = home_blks_agst_avg_last5 - away_blks_agst_avg_last5
  ,blks_diff_avg_last5_diff = home_blks_diff_avg_last5 - away_blks_diff_avg_last5
  ,blks_diff_total_last5_diff = home_blks_diff_total_last5 - away_blks_diff_total_last5
  ,GvA_avg_last5_diff = home_GvA_avg_last5 - away_GvA_avg_last5
  ,TkA_avg_last5_diff = home_TkA_avg_last5 - away_TkA_avg_last5
  ,ENG_avg_last5_diff = home_ENG_avg_last5 - away_ENG_avg_last5
  ,ENG_opp_avg_last5_diff = home_ENG_opp_avg_last5 - away_ENG_opp_avg_last5
  ,MsS_avg_last5_diff = home_MsS_avg_last5 - away_MsS_avg_last5
  ,PP_Opp_avg_last5_diff = home_PP_Opp_avg_last5 - away_PP_Opp_avg_last5
  ,`PP%_last5_diff` = `home_PP%_last5` - `away_PP%_last5`
  ,PP_Opp_agnst_avg_last5_diff = home_PP_Opp_agnst_avg_last5 - away_PP_Opp_agnst_avg_last5
  ,`PenaltyKill%_last5_diff` = `home_PenatlyKill%_last5` - `away_PenatlyKill%_last5`
  ,W_last5_diff = home_W_last5 - away_W_last5
  ,L_last5_diff = home_L_last5 - away_L_last5
  ,OT_last5_diff = home_OT_last5 - away_OT_last5
  ,Pts_last5_diff = home_Pts_last5 - away_Pts_last5
  ,`Pt%_last5_diff` = `home_Pt%_last5` - `away_Pt%_last5`
  ,SO_last5_diff = home_SO_last5 - away_SO_last5
  ,OT_win_last5_diff = home_OT_win_last5 - away_OT_win_last5
  
)
```

```{r}
library(RSelenium)
library(rvest)
library(dplyr)
library(xml2)
library(xgboost)
library(lubridate)
library(caret)
library(stringr)
library(janitor)
library(e1071)

#Make Predictions
GameData <- TotalPredictionData_Final_v2 %>% 
  select(-c(GameKey, Date, HomeTeam, AwayTeam, Season, Total_Goals))


load("Hockey_Prediction_Model.RData")
load("SVM_Model.RData")



#SVM predictions
svm_preds <- predict(classifier_prob, GameData 
                     , probability = TRUE
                     )

predict_probs <-data.frame( attr(svm_preds, "probabilities")) %>% rename("SVM_Home" = X1, "SVM_Away" = X0)

predict_probs <- predict_probs %>% mutate(predictSVM_HomeTeamWin = case_when(SVM_Home >= 0.5 ~ 1, SVM_Home < 0.5 ~ 0))


#XGBoost predictions
dtest <- xgb.DMatrix(data = as.matrix(GameData %>% select(-HomeTeamWin)), label = GameData$HomeTeamWin)

boost_preds <- predict(bst_final, dtest)

boost_pred_class <- rep(0, length(boost_preds))
boost_pred_class[boost_preds >= 0.5] <- 1


TotalPredictions <- cbind(GameKey = TotalPredictionData_Final_v2$GameKey, predict_probs, boost_pred_class, boost_preds) %>% select(GameKey, SVM_Home, boost_preds_Home = boost_preds)






 
```

```{r}
#Boston Bruins  @  Buffalo Sabres   2014-10-18
#Arizona Coyotes @ Dallas Stars 2024-03-20

#Need to adjust gamekey for spaces and Montreal's accent
library(stringr)
library(stringi)

Clean2024_2025_Data_3 <-
left_join(PredictionData_3,
TotalPredictions %>% mutate(GameKey = str_squish(GameKey)) %>% mutate(GameKey = stri_trans_general(str = GameKey, id = "Latin-ASCII")),
by = join_by(GameKey)
)
```


```{r}
save(Clean2024_2025_Data_3, file = "Clean2024_2025_Data_3.RData")
```













